---
title: "RO Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    # vertical_layout: scroll
    # self_contained: false
---


<style> 

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 80px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table { 
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)

```

Staffing page
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated every 2 hrs.

```{r Staffing-Page-knit, out.width='100%'}

#get the name of the html file that exists.
Staffing_File<-list.files(path=RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern= 'EOI',full.names = TRUE)

#if it exists, output as an include url.

if (length(Staffing_File)==1){
  include_url(Staffing_File,height='100%')
} else {
  cat("No staffing page found")
}


```




Pre-poll Votes
==============================================================


Row {data-height = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated twice daily.


```{r Pre-Poll-Page-knit, out.width='100%'}

#get the name of the html file that exists.
PrePoll_File<-list.files(path=RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern= 'Pre-Poll',full.names = TRUE)

#if it exists, and pre-poll data is for right event, output as an include url.

if (length(PrePoll_File)==1 &
    event_group_ID %in% Pre_Poll_Data$EventID ){
  include_url(PrePoll_File,height='100%')
} else {
  cat("No pre-poll data available yet")
}


```




Dec Votes 
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated twice daily.

```{r DecVote-Page-knit, out.width='100%'}

#get the name of the html file that exists.
DecVote_File<-list.files(path=RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern= 'DecVote',full.names = TRUE)

#if it exists, output as an include url.

if (length(DecVote_File)==1 &
    event_group_ID %in% Dec_Vote_Data$EventID ){
  include_url(DecVote_File,height='100%')
} else {
  cat("No Dec Vote data available yet")
}


```




Ballot Track
==============================================================



Column {data-width = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated twice daily.




```{r BallotTrack-Page-knit, out.width='100%'}

#get the name of the html file that exists.
BallotTrack_File <- list.files(path = RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern = 'BallotTrack', full.names = TRUE)

#if it exists, output as an include url.

if (length(BallotTrack_File) == 1 &
    event_group_ID %in% Ballot_Track_Data$EventID ) {
  include_url(BallotTrack_File,height='100%')
  
} else {
  cat("No ballot track data available yet")
}


```


Initial Count
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated twice daily.

```{r InitialCount-Page-knit, out.width='100%'}

#get the name of the html file that exists.
InitialCount_File <- list.files(path = RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern = 'InitialCount', full.names = TRUE)

InitialEvent <- Councillor_initial %>%
  mutate(EventID = str_sub(CONTESTID,start=1,end=6)) %>%
  select(EventID) %>%
  distinct()


#if it exists, output as an include url.

if (length(InitialCount_File) == 1 & event_group_ID %in% InitialEvent) {
  include_url(InitialCount_File,height='100%')
  
} else {
  cat("No Initial Count data available yet")
}


```



Check Count
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------
<br>
<br>
Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

Data is **not** live. It will be updated twice daily.

```{r CheckCount-Page-knit, out.width='100%'}

#get the name of the html file that exists.
CheckCount_File <- list.files(path = RO_File_Subs, 
                     #get the one with EOI in the name
                     pattern = 'CheckCount', full.names = TRUE)

CheckEvent <- Councillor_check %>%
  mutate(EventID = str_sub(CONTESTID,start=1,end=6)) %>%
  select(EventID) %>%
  distinct()
#if it exists, output as an include url.

if (length(CheckCount_File) == 1 &  event_group_ID %in% CheckEvent) {
  include_url(CheckCount_File,height='100%')
  
} else {
  cat("No Check Count data available yet")
}


```