---
title: "Home"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

<style type="text/css">

body {
padding-top: 115px !important;
font-family: Helvetica;
color: #000000;
}

.navbar-inverse {
padding-top: 10px !important;
background-color: #ffffff !important;
border-color: #000000;
font-size:  9pt !important;
font-family: Helvetica;
color: #000000;
min-height: 100px !important;
height: 100px !important;
}

.navbar-inverse .navbar-nav > li > a {
color: #000000;
padding-top: 25px !important;
}

.row {
width: 100% !important;
}

.main-container {
max-width: 1800px;
margin-left: auto;
margin-right: auto;
margin-left:-15px !important;
font-family: Helvetica;
color: #000000;
}

</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Row {data-height=300}
-----------------------------------------------------------------------


### This dashboard tracks the hire status, projected voters and Procurement for all Venues
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Venue Procurement", 
                        icon  = "fa-building", 
                        href  = "01-Venues-and-procurement.html", 
                        color = "#8DD3C7")

```


### This dashboard tracks the staff recruitment, training and language status for all RO Offices
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Staffing", 
                        icon  = "fa-users", 
                        href  ="02-Staffing.html", 
                        color = "#D95F02")


```


### This dashboard tracks the Daily Pre-Poll attendance Votes per Venue
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Pre-poll Voting", 
                        icon = "fa-user-check", 
                        href = "03-Early-Voting.html", 
                        color = "#BEBADA")

```


Row {data-height=300}
-----------------------------------------------------------------------


### This dashboard tracks the daily declaration votes (attendance and Postal) per Venue
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Dec Vote Processing", 
                        icon  = "fa-envelope-open-o", 
                        href  = "04-Declaration-Voting.html", 
                        color = "#FB8072")

```



### This dashboard tracks the daily nominations by Registered Political Parties
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Candidate Nominations", 
                        icon = "fa-user-tie", 
                        href = "05-Candidate-Nominations.html", 
                        color = "#80B1D3")

```



### This dashboard tracks the daily processing of How-To-Vote material submitted by Registered Political Parties
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("How to Vote", 
                        icon  = "fa-file-signature", 
                        href  = "06-How-to-Vote.html", 
                        color = "#FDB462")

```


Row {data-height=300}
-----------------------------------------------------------------------


### This dashboard tracks the progress of Cartons of ballot Papers being scanned, from the printer to warehouse
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("BallotTrack", 
                        icon = "fa-truck",
                        href = "08-Ballot-Track.html", 
                        color = "#FCCDE5")
```


### This dashboard tracks the processing of election results
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Count Centre Operations", 
                        icon = "fa-warehouse",
                        href = "11-Count-centre.html", 
                        color = "#58D68D")
```


### This dashboard tracks the processing of election results
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Results Processing", 
                        icon = "fa-calculator",
                        href = "10-RMT.html", 
                        color = "#D9D9D9")
```




