---
title: "RMT"
output: 
  # flexdashboard::flex_dashboard:
  #   orientation: rows
---

<style type="text/css">

body {
padding-top: 115px !important;
font-family: Helvetica;
color: #000000;
background: #ffffff;
}

.navbar-inverse {
padding-top: 10px !important;
background-color: #ffffff !important;
border-color: #000000;
font-size:  9pt !important;
font-family: Helvetica;
color: #000000;
min-height: 100px !important;
height: 100px !important;
}

.navbar-inverse .navbar-nav > li > a {
color: #000000;
padding-top: 25px !important;
}

.row {
width: 100% !important;
}

.main-container {
max-width: 1800px;
margin-left: auto;
margin-right: auto;
margin-left:-15px !important;
font-family: Helvetica;
}

.fa-rho:before {
    font-weight: 700;
    content: '\03c1';
}

#f-drive-backup-summary {

color : #ffffff;
box-shadow: none;

}

a:hover {
  background-color: white;
}

.value-box .icon i.fa.fa-camera{
    
    color: #ffffff; /*red*/
  
}

a:hover {
  display:none;
}


</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Column {data-width=3}
-----------------------------------------------------------------------


<!-- ### Pre poll - #potentially remove -->
<!-- ```{r echo=FALSE} -->

<!-- ## Put the description of the dashboard on the main tab -->
<!-- flexdashboard::valueBox("PrePoll",  -->
<!--                         icon  = "fa-random",  -->
<!--                         href  = "10-RMT_index-01-PrePoll.html",  -->
<!--                         color = "#8DD3C7") -->

<!-- ``` -->


### Initial Count - LG2101
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Initial Count", 
                        icon  = "fa-user-plus", 
                        href  ="10-RMT_index-01.5-Initial-Count.html", 
                        color = "#D95F02")


```


<!-- Row {data-height=300} -->
<!-- ----------------------------------------------------------------------- -->


### Batching and data entry - LG2101
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("Check Count", 
                        icon  = "fa-envelope-open-o", 
                        href  = "10-RMT_index-04-Check-count.html", 
                        color = "#FB8072")

```



### Duty of care calls and EMA initial count completion times - LG2101
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("WHS Principles",
                        icon = "fa-user-o",
                        href = "10-RMT_index-05-WHS-Principles.html",
                        color = "#80B1D3")

```


### Extra Pre-poll issue AoBP - LG2101
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("AoBP",
                        icon = "fa-rho",
                        href = "10-RMT_index-06-AoBP.html",
                        color = "#6fbb56")

```




### F drive backup summary
```{r echo=FALSE}

## Put the description of the dashboard on the main tab
flexdashboard::valueBox("F: drive",
                        icon = "fa-camera",
                        href = "10-RMT_index-07-FDrive.html",
                        color = "#FFFFFF")

```


Column {data-width=5}
-----------------------------------------------------------------------


