---
title: " Venues and procurement "
output: 
  flexdashboard::flex_dashboard:
    orientation: columns


---


<style>


.bluebox {

 background-color: #2571bd;
    border: solid #ddd 1px;
    font-size: 15px;
    height:40px;
    padding:5px;
    margin-bottom: 5px;
    border-radius:5px;
	color: #f9f9f9;
	
	}

body {

  padding-top: 60px !important;
  
}

h1 {
    font-size: 25px;
}

.leaflet-control-attribution{
display:none;
}



.btn {
    background-color: DodgerBlue;
    border: none;
    color: white;
    cursor: pointer;
    font-size: 15px;
}

.btn:hover {
    background-color: #3d6ece;
}

table { 
    border-spacing: 5px;
    border-collapse: separate;
    border:1px
}

.p {
margin-top:20px

}

div.text1 {
border: solid #ddd 1px;
background-color: #f9f9f9;
padding-left:20px;
padding-top:10px;
padding-bottom:10px;
margin-top:20px;
margin-bottom:20px;
border-radius:3px;
}



div.header{

padding-top:30px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
    position: sticky;
    bottom: 0;
    width: 100%;
	height:30px;
    background-color: #2b6eda;
    color: white;
    text-align: center;
}

div.main-wrapper {
    position: relative;
}


div.leaflet-control-attribution{
	display:none;
}

div.leaflet-container {
    background: #0184a9;
}



</style>




```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

Overall Summary
=========================================

Column {data-width=200}
-----------------------------------------------------------------------

Last update: 
**`r Sys.time()`**

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}


filter_Area

filter_VenueType

filter_projection


filter_Status

```



Column 
-----------------------------------------------------------------------

<table class='ValueBox'>
<tr>

<td width="200" class="bluebox">
 <span>Unique Venues: </span><br>**`r summarywidget(procurement_sd, selection=~LocationStatusCode!="It's Away")`**
</td>

<td width="200" class="bluebox">
 <span>Missing GeoCodes: </span><br>**`r summarywidget(procurement_sd, selection=~GeoStatus =='Missing', digits=0)`**
</td>

<!-- <td width="200" class="bluebox">
 <span>Check Projection: </span><br>**`r summarywidget(procurement_sd, selection=~ProjectedVoters==0)`**
</td>
--> 

<td width="200" class="bluebox">
 <span>Procurement incomplete: </span><br>**`r summarywidget(procurement_sd, selection=~LocationStatusCode != 'Hire Agreement Signed')`**
</td>


</tr>
</table>



### Data 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}


datatable(procurement_sd, rownames= FALSE, extensions = 'Buttons', filter = 'top',
          options = list(
            pageLength = 10
            ,dom = 'tip'

          #  ,lengthMenu = c(10, 20, 50, 100)
            ),
          height = '600px')



```

### Procurement Summary 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}

datatable(Procurement_report, rownames= FALSE, extensions = 'Buttons', filter = 'top',
          options = list(
            pageLength = 8
            ,dom = 'tip'
          #  ,lengthMenu = c(10, 20, 50, 100)
            ),
          height = '400px')

```



Column 
-----------------------------------------------------------------------


### Search for venue of interest 
```{r echo=FALSE, out.height="50%", message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA}

VenueMap


```

Council Procurement Summary
=========================================
Column
----------------------------------------------------------------------
Last update: 
**`r Sys.time()`**

### Procurement Summary 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, comment = NA, out.width=="100%"}
datatable(Procurement_report_by_area, rownames= FALSE, extensions = 'Buttons', filter = 'top',
          options = list(
            pageLength = 10
            ,dom = 'Btip',
            ,scrollY = '100%'

            buttons=c( 'csv', 'excel')
             # ,lengthMenu = c(10, 20, 50, 100)
          ))

```



