---
title: ""
output: flexdashboard::flex_dashboard
---
<style>

.navbar-inverse .navbar-nav>li>a {

color:#000000;
}


.tab-content {

	padding-top:30px;


}

.container-fluid {
	
	background-color:white;
	padding-bottom:0px;
	
}

.bluebox {
 background-color: #2571bd;
    border: solid #ddd 1px;
    font-size: 15px;
    height:40px;
    padding:5px;
    margin-bottom: 5px;
    border-radius:5px;
	color: #f9f9f9;
	}

body {
    padding:0px;
    padding-top:20px;

 background-color: white;

}

h1 {
    font-size: 25px;
}

.leaflet-control-attribution{
display:none;
}

.leaflet-container {
 background-color: white;


}


.leaflet-popup-content-wrapper {
 background: #eff4ef2e;
 box-shadow:0 3px 10px rgba(0, 0, 0, 0);

}


.gmisc_table {

 width:max-content;


}


.btn {
    background-color: DodgerBlue;
    border: none;
    color: white;
    cursor: pointer;
    font-size: 15px;
}

.btn:hover {
    background-color: #3d6ece;
}

table { 
    border-spacing: 5px;
    border-collapse: separate;
    border:1px
}

.p {
margin-top:20px

}

div.text1 {
border: solid #ddd 1px;
background-color: #f9f9f9;
padding-left:20px;
padding-top:10px;
padding-bottom:10px;
margin-top:20px;
margin-bottom:20px;
border-radius:3px;
}



div.header{

padding-top:30px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
    position: sticky;
    bottom: 0;
    width: 100%;
	height:30px;
    background-color: #2b6eda;
    color: white;
    text-align: center;
}

div.main-wrapper {
    position: relative;
}

<!-- .navbar-fixed-top { -->

<!-- visibility: hidden; -->

<!-- } -->



</style>

EOI Summary
=====================================

Column {data-width=30}
-------------------------------------
### -Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
```{r, echo=FALSE, warning=FALSE, message=FALSE}

Summary_status_table
txt <- c('Total = OPEN + OFFERED + EMPLOYED'
         ,'Completion rate = EMPLOYED/Total'
         ,'Number of OPEN positions is dependent on RO opening up the position in the system')
cat(txt, sep="\n")

```   


Column {data-width=18}
-------------------------------------
### New Applicants that had no past election experiences amongest applications and hired groups

<div class="expdiv">
<table>
<tr>
<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}
gauge(gauge_exp, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))
```
<span class="demospan">Applicants</span>
</td>
<td>
```{r}
gauge(gauge_exp_hired, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))
```
<span class="demospan">Hired</span>
</td>
</tr>
</table>
</div>

    
### Position by Fill Status - Election Day
<div class="expdiv">
<table>
<tr>
<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}
gauge(gauge_ed_hired, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))
```
<span class="demospan">Hired</span>
</td>
<td>
```{r}
gauge(gauge_ed_trained, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))
```
<span class="demospan">Trained</span>
</td>
</tr>
</table>
</div>



Column {data-width=30}
-------------------------------------
### Number of Aboriginal and Torres Straight Islander Employees that are hired
```{r, echo=FALSE, warning=FALSE, message=FALSE}
gauge(gauge_ATSI_hired, min = 0, max = nrow(ATSI), symbol = '', gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)))
```


### Age distribution among applicants
```{r}

   if (nrow(age_dist) >0) {
   
      hchart(agehist,  color = "lightblue", name = "Age bracket of applicants")     

   }

```

Position Summaries 
=====================================

Column {data-width=30}
-------------------------------------
### by RO
```{r}

datatable(RO_Summary,
           extensions = 'Buttons',
                  rownames = FALSE,
                  options = list(dom = 'Bfrtip'
                                ,scrollY = '100%'

                             #,pageLength = 10
                             #,lengthMenu = c(10, 25, 50)
                             ),
                              height = '480px',
                              width='650px')
   if (nrow(age_dist) >0) {
   
     hchart(agehist)
   }
```

Column {data-width=35}
-------------------------------------
### by LGA
```{r}

datatable(LGA_Summary,
           extensions = 'Buttons',
                  rownames = FALSE,
                  options = list(dom = 'Bfrtip'
                                ,scrollY = '100%'

                             #,pageLength = 10
                             #,lengthMenu = c(10, 25, 50)
                             ),
                              height = '480px',
                              width='650px')
   if (nrow(age_dist) >0) {
   
     hchart(agehist)
   }
```





Training Status and Languages
=====================================

Column {data-width=3}
-------------------------------------
### Applicant Training Status Election Day
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}

training_ed_stack


```

### Applicant Training Status Non-Election Day
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}


training_else_stack

```

Column {data-width=3}
-------------------------------------
### Applicant Language Proficiency
```{r, fig.width=19, fig.height=11, echo=FALSE, warning=FALSE, message=FALSE}
if (nrow(table_lan) > 0) {
  

    hchart(table_lan, "column", hcaes(x = "SECONDLANGUAGE", y = "Count", group = "Status")) %>%
    hc_plotOptions(column = list(stacking = "normal"))
}
  

```


Election day Venue level numbers
=====================================

Column {data-width=3}
-------------------------------------
### RO office - Venue hiring status
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}

datatable(Opened_Positions %>% ungroup() %>% dplyr::select(RO_Office, everything(),-StreetAddressID, -EventID), 
              rownames= FALSE, extensions = 'Buttons',
              options = list(
                            dom = 'Blfrtip'
                            ,scrollY = '100%'

                            ,pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')


```