---
title: "Pre-poll"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
 #   self_contained: false
---


<style>

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 115px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table {
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>





<!-- set global options here -->
```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
source(paste0(root_dashboard,  '01 R scripts/Functions/dashboard_plotting_library.R'))

```



Headlines
==============================================================


Column {data-width=4}
-----------------------------------------------------------------------

### Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm. 

```{r Prepoll Headlines, echo = FALSE}

if (Pre_Poll_Open){
PrePollHeadline
} else {
  print("No Pre-Polls Open")
}

```

<strong>*Note:</strong> Most Over and Under Projected chosen from venues with Projections >100



Column {data-width=5}
-----------------------------------------------------------------------
### Cumulative prepoll
<!-- fig.height = 15, fig.width = 20,  -->
```{r Total Votes By Day, echo = FALSE, fig.height=8,fig.width=10,warning = FALSE, message = FALSE}
if (Pre_Poll_Open){
# group_line_plot(df         = daily_cumulative_pre_poll,
#                 title      = 'All Venues - Total Votes issued by day',
#                 subtitle   = '',
#                 caption    = '',
# 
#                 xvar       = 'Day',
#                 yvar       = 'Total_cum_count',
#                 group_var  = 'Status',
# 
#                 tsize      = 20,
#                 capt_size  = 15,
#                 xsize      = 20,
#                 ysize      = 20,
#                 ycol       = 'black',
#                 line_size  = 2.5,
#                 point_size = 3.5,
# 
#                 lab_size   = 3,
#                 leg_size   = 20,
#                 leg_pos    = 'bottom',
#                 mar        = 1,
# 
# 
#                 ylab       = 'Pre-poll Votes',
#                 xlab       = 'Days of Pre-polling',
#                 lab_angle  = 0)# %>% ggplotly(tooltip=c("x", "y","group"))
  
  
  
hchart(daily_cumulative_pre_poll %>%
         rename(Date=VOTEPROCESSEDDATE), 'line',hcaes(x=Date, y=Total_cum_count, group = Status)) %>%
  hc_title(
    text = 'Cumulative total early votes taken',
    style = list(
      color = "black",
      fontSize = "25px"
    )) %>%
  hc_yAxis(title = list(text='Pre-poll'),
           min =0,
    style = list(
      color = "black",
      fontFamily = "Griffy",
      fontSize = "25px")) %>%
  hc_tooltip(table = TRUE, sort = FALSE) %>%
  hc_legend(enabled = F) %>%
  hc_size(width = 1200,
          height = 750) %>%
  hc_tooltip(crosshairs=c(TRUE,TRUE)) %>%
  hc_add_theme(hc_theme_google())

  

} else {
  print("No Pre-Polls Open")
}

# ggplot(data=daily_cumulative_pre_poll,aes(x=Day,y=Total_cum_count))+
#   geom_line(aes(group=Status))



```


Venue loads
==============================================================


Column {data-width = 800}
-----------------------------------------------------------------------


```{r Venue Voting Loads, fig.width=20, echo=FALSE, warning=FALSE, message=FALSE}

# nrow(venue_total_load %>% distinct());nrow(venue_total_load)
if (Pre_Poll_Open){
datatable(venue_total_load %>% 
            arrange(-`Voting Load Prop`) %>% 
            select(Day, everything()), 
            
            
            
            
            # mutate(`Voting Load Prop`=
            #          percent(`Voting Load Prop`, accuracy=0.1)),
            
    
          
          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(
            
            ## move captions to the bottom
            style = 'caption-side: bottom; text-align: center;',
            "Daily venue-level measure of resourcing. 
                        Voting load proportion = Early Voting/Projected Vote  
                        (i.e. the proportion, 200% = double the expected 
                        amount of people showed up to that venue on that day)"),
          
          options = list(
            pageLength = 15
            ,dom = 'tip',
            scrollY = '100%'),
          
          height = '600px')%>%
    
  
  #set voting load to a percentage
  formatPercentage(c('Voting Load Prop'),1)

} else {
  print("No Pre-Polls Open")
}


```




Daily Totals 
========================================================


```{r Daily Totals, echo=FALSE, warning=FALSE, message=FALSE}
## nrow(Markoffs_day_contests %>% distinct());nrow(Markoffs_day_contests)
if (Pre_Poll_Open) {
datatable(Markoff_days_contests_proj %>% 
            left_join(Contest_Status,
                      by = c("ISSUINGAREA" = "areacode",
                             "CONTESTAREA" = "contestareacode",
                             "CONTESTTYPECODE" = "contesttypecode")) %>%
            filter(CONTESTSTATUSTYPECODE == "Contested") %>%
            select(-CONTESTSTATUSTYPECODE) %>%
            arrange(-PRE_POLL_MARKOFFS)%>%
            
            #reformat date for ease or reading
            mutate(VOTEPROCESSEDDATE = as.Date(VOTEPROCESSEDDATE),
                   VOTEPROCESSEDDATE = format(VOTEPROCESSEDDATE,
                                              format = "%d-%b-%y"))%>%
            
            #rename columns for ease of reading
            rename(Council               = ISSUINGAREA,
                   Ward                  = CONTESTAREA,
                   Venue                 = VENUENAME,
                   `Election Type`       = CONTESTTYPECODE,
                   `Date of Vote`        = VOTEPROCESSEDDATE,
                   `Pre-poll Votes`         = PRE_POLL_MARKOFFS,
                   `Projected Votes`     = Projection)%>%
            select(Day, `Date of Vote`,everything()),
          
          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(
            
            #move captions to the bottom
            
            style = 'caption-side: bottom; text-align: center;',
            'Daily Pre-Poll Votes Per Venue'),
          
          options    = list(
            pageLength = 15
            , dom = 'tip',
            scrollY = '100%'),
          
          height     = '600px')%>%
  
  #set voting load to a percentage
  formatPercentage(c('Voting Load Prop'),1)
} else {
  print("No Pre-Polls Open")
}

  
  
```


Cumulative Totals
========================================================


```{r cumulative Pre-Poll votes to date, echo=FALSE, warning=FALSE, message=FALSE}
## nrow(Markoff_LGA_totals %>% distinct());nrow(Markoff_LGA_totals)
if (Pre_Poll_Open){
datatable(Markoff_LGA_totals %>% 
            left_join(Contest_Status,
                      by = c("LGA" = "areacode",
                             "Contest_area" = "contestareacode",
                             "Contest_type" = "contesttypecode")) %>%
            filter(CONTESTSTATUSTYPECODE == "Contested") %>%
            select(-CONTESTSTATUSTYPECODE) %>%
            arrange(-`Pre-poll Votes`)%>%
            
            
            ## Rename columns for ease of reading
            rename(Council               = LGA,
                   Ward                  = Contest_area,
                   `Election Type`       = Contest_type),
          
          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(
            
            ## Move captions to the bottom
            style = 'caption-side: bottom; text-align: center;',
            paste0('Cumulative Pre-Poll Vote Total Per Venue. All Votes and Projections are up to ',Last_Date,".")),
          
          options    = list(
            pageLength = 15
            , dom = 'tip',
            scrollY= '100%'),
          
          height     = '600px')%>%
  
  #set voting load to a percentage
  formatPercentage(c('Voting Load Prop'),1)

} else {
  print("No Pre-Polls Open")
}


```




