---
title: 'Nominations'
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    self_contained: false
---


<style>

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 115px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table {
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}


</style>


<!-- set global options here? -->
```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, warning = FALSE, fig.fullwidth = TRUE)
library(ggplot2)
# source('./01 R scripts/Functions/dashboard_plotting_library.R')

```




Headlines
==============================================================


Column {data-width = 300}
-----------------------------------------------------------------------


### Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
Data is **not** updated in real time. Updates occur every hour between 8am and 6pm. 


```{r Headline Table}

NomsHeadlineTable_flex 

```


Column {data-width = 700}
-----------------------------------------------------------------------


```{r, fig.width=10, fig.height=6, fig.align = 'center'}
if(nrow(council_mayor_count_date) > 1 & 'Date' %in% names(council_mayor_count_date)) {
  
  message('Creating graph')
  
  ## Create data ends 
  d_ends <- council_mayor_count_date %>% 
    group_by(CONTESTTYPECODE) %>% 
    top_n(1, Date) %>% 
    pull(Noms_cum_count)
  
  ## Create ggplot
  lodged.nom.date <- council_mayor_count_date %>% 
    ggplot(aes(Date, Noms_cum_count, color = CONTESTTYPECODE)) +
    geom_line(size = 2, alpha = .8) +
    theme_light(base_size = 16) +
    scale_y_continuous(sec.axis = sec_axis(~ ., breaks = d_ends)) +
    
    ##
    labs(title = paste("Lodged Nominations by Date (up to " , 
                       format(Sys.Date(), format = "%d-%b-%y"),")", "\n", sep = ""),
         x = '', #"\nDate lodged",
         y = "Total Nominations\n\n") +  
    
    ## Create the themes
    theme_light(base_size = 16) +
    
    theme(axis.title.x = element_text(face   = "bold", colour = "black", size = 10),
          axis.text.x  = element_text(size   = 15, angle = 45, hjust = 1, vjust = 0.5),
          axis.text.y  = element_text(size   = 15),
          axis.title.y = element_text(face   = "bold", 
                                      colour = "black", 
                                      size   = 15),
          legend.position  = 'bottom',
          legend.title     = element_blank(),
          
          panel.grid.major = element_line(size   = 0.5, linetype = 'solid',
                                          colour = "grey"), 
          panel.grid.minor = element_line(size   = 0.5, linetype = 'solid',
                                          colour = "grey"))
  
  lodged.nom.date
  
} else {
  message('Incoming Nominations are being processed')
}


```



```{r, fig.width=10, fig.align = 'center'}
## Council nominations by type
if(nrow(overall_incomplete_nominations) > 0) {
  total.noms.count  <- dash_bar_chart_xvar_facet(df        = overall_incomplete_nominations,
                                                 
                                                 title     = '',
                                                 caption   = '',
                                                 
                                                 xvar      = 'Status',
                                                 yvar      = 'Nominations',
                                                 group_var = 'Type',
                                                 colours   =  c('Incoming'   = "#7570B3", 
                                                                'Processing' = "#1B9E77",  
                                                                'Pending'    = "#1B9E77", 
                                                                'Rejected'   = "#1B9E77", 
                                                                'Withdrawn'  = "#1B9E77",             
                                                                'Accepted'   = "#1B9E77"), 
                                                 
                                                 tsize     = 15,
                                                 capt_size = 15,
                                                 xsize     = 15,
                                                 ysize     = 15,
                                                 ycol      = 'black',
                                                 lab_size  = 5,
                                                 leg_pos   = 'none',
                                                 axis_size = 1,
                                                 h_just    = -0.3,
                                                 
                                                 ymin      = 0,
                                                 ymax      = max(overall_incomplete_nominations$Nominations) +
                                                   (max(overall_incomplete_nominations$Nominations))*0.2,
                                                 ylab      = '',
                                                 xlab      = '', 
                                                 mar       = 0.5,
                                                 pan_mar   = 0.5,
                                                 wrap_scale = "free",
                                                 facet_cols = 1,
                                                 facet_rows = 1)
  
  total.noms.count 
  
} else {
  print('Insufficient lodged Nominations, try again later :]')
}

```





Nomination count by RPP
=====================================


Column
-------------------------------------



Column
-------------------------------------


### **Count of approved nominations by Registered Political Parties**

```{r}

if(nrow(Party_Nominations) > 0) {
  
  datatable(Party_Nominations, 
            
            rownames     = FALSE, 
            extensions   = 'Buttons', 
            filter       = 'top',
            
            options      = list(
              pageLength = 50, 
              dom        = 'tip'))
  
} else {
  print('Insufficient Party Nominations, try again later :]')
}

```


Column
-------------------------------------




Nomination count by Status
=====================================


Column {data-width = 1}
-----------------------------------------------------------------------


Column {data-width = 8}
-----------------------------------------------------------------------


```{r, fig.width=15, fig.height=6, fig.align = 'center'}
if(nrow(combined_status_counts) > 0) {
  overall.noms.count <- dash_bar_chart_xvar_facet(df        = combined_status_counts,
                                                  
                                                  title     = '',
                                                  caption   = '',
                                                  
                                                  xvar      = 'Status',
                                                  yvar      = 'Nominations',
                                                  group_var = 'Type',
                                                  colours   =  c('Incoming'   = "#7570B3", 
                                                                 'Processing' = "#A6761D",  
                                                                 'Pending'    = "#666666", 
                                                                 'Rejected'   = "#E7298A", 
                                                                 'Withdrawn'  = "#D95F02",             
                                                                 'Accepted'   = "#1B9E77"), 
                                                  
                                                  tsize     = 15,
                                                  capt_size = 10,
                                                  xsize     = 12,
                                                  ysize     = 12,
                                                  ycol      = 'black',
                                                  lab_size  = 5,
                                                  leg_pos   = 'none',
                                                  axis_size = 1,
                                                  h_just    = -0.3,
                                                  
                                                  ymin      = 0,
                                                  ymax      = max(combined_status_counts$Nominations) +
                                                    (max(combined_status_counts$Nominations))*0.2,
                                                  ylab      = 'Total Nominations',
                                                  xlab      = '', 
                                                  mar       = 0.5,
                                                  pan_mar   = 0.5,
                                                  wrap_scale = "free",
                                                  facet_cols = 2,
                                                  facet_rows = 2)
  
  overall.noms.count
  
} else {
  print('Insuficient lodged Nominations, try again later :]')
}


```


**This graph displays the total nomination by status for councillor, mayor, groups and an overall total of both mayor and councillor.** 
Status Definitions.
**Accepted:**   Nomination Accepted
**Withrdrawn:** Nomination withdrawn by Candidate \
**Rejected:**   Nomination Rejected
**Pending:**    Nomination Currently awaiting fixes from the candidate
**Processing:** With the NSWEC processing team for review 
**Incoming:**   Nomination has been created by not yet completed or paid for



Column {data-width = 1}
-----------------------------------------------------------------------



Confirmed Councillor Nominations by LGA
=====================================


Column {data-width = 800}
-----------------------------------------------------------------------

### **This table shows the total number of Accepted Councillor nominations by Local Government Area.**


```{r}
if(nrow(Confirmed_Council_Noms) > 0) {
  
  ## Arrange the table by the contests with shortfalls - i.e. positive numbers
  datatable(Confirmed_Council_Noms %>% filter(`Contest Type` == "Councillor") %>% arrange(-Shortfall), 
            
            rownames   = FALSE, 
            extensions = 'Buttons', 
            filter     = 'top',
            
            options = list(
              pageLength = 50, dom = 'tip'))
  
} else {
  print('Insuficient lodged Nominations, try again later :]')
}


```



Column {data-width = 300}
-----------------------------------------------------------------------



```{r, fig.width=12, fig.height = 30, fig.align = 'center'}
# if(class(event_group_ID) != "NULL" & unique(noms_extract$DATEOFLODGEMENT) !="") {

if(nrow(Confirmed_Council_Noms) > 0) {
  
  councillor.councils.count  <- dash_bar_chart_yvar_samecol_facet(df = Confirmed_Council_Noms %>% 
                                                                    filter(`Contest Type` == "Councillor"),
                                                                  title     = '',
                                                                  caption   = '',
                                                                  
                                                                  xvar      = 'Contest Area',
                                                                  yvar      = 'Accepted Nominations',
                                                                  ordervar  = 'Accepted Nominations',
                                                                  
                                                                  group_var = 'Contest Type',
                                                                  colour    =  c("deepskyblue"), 
                                                                  
                                                                  tsize     = 15,
                                                                  capt_size = 10,
                                                                  xsize     = 12,
                                                                  ysize     = 7,
                                                                  ycol      = 'black',
                                                                  lab_size  = 5,
                                                                  leg_pos   = 'none',
                                                                  axis_size = 1,
                                                                  h_just    = -0.3,
                                                                  mar       = 0.5,
                                                                  pan_mar   = 0.5,
                                                                  
                                                                  ymin      = 0,
                                                                  ylab      = 'Total Accepted Nominations',
                                                                  xlab      = '',
                                                                  wrap_scale = "free",
                                                                  facet_cols = 1,
                                                                  facet_rows = 1)
  
  
  councillor.councils.count 
  
} else {
  print('No Confirmed Council Nominations, try again later :]')
}



```



Confirmed Mayoral Nominations by LGA
=====================================


Column {data-width = 800}
-----------------------------------------------------------------------

### **This table shows the total number of Accepted Mayoral nominations by Local Government Area.**


```{r}
if(nrow(Confirmed_Council_Noms) > 0) {
  
  ## Arrange the table by the contests with shortfalls - i.e. positive numbers
  datatable(Confirmed_Council_Noms %>% filter(`Contest Type` == "Mayor") %>% arrange(-Shortfall), 
            
            rownames   = FALSE, 
            extensions = 'Buttons', 
            filter     = 'top',
            
            options = list(
              pageLength = 50, dom = 'tip'),
            height = '600px')
  
} else {
  print('No Confirmed Council Nominations, try again later :]')
}

```



Column {data-width = 300}
-----------------------------------------------------------------------



```{r, fig.width=12, fig.height=20,fig.align = 'center'}
if(nrow(Confirmed_Council_Noms) > 3) {
  
  mayor.councils.count  <- dash_bar_chart_yvar_samecol_facet(df = Confirmed_Council_Noms %>% 
                                                               filter(`Contest Type` == "Mayor"),
                                                             title     = '',
                                                             caption   = '',
                                                             
                                                             xvar      = 'Contest Area',
                                                             yvar      = 'Accepted Nominations',
                                                             ordervar  = 'Accepted Nominations',
                                                             
                                                             group_var = 'Contest Type',
                                                             colour    =  c("deepskyblue"), 
                                                             
                                                             tsize     = 15,
                                                             capt_size = 10,
                                                             xsize     = 12,
                                                             ysize     = 12,
                                                             ycol      = 'black',
                                                             lab_size  = 5,
                                                             leg_pos   = 'none',
                                                             axis_size = 1,
                                                             h_just    = -0.3,
                                                             mar       = 0.5,
                                                             pan_mar   = 0.5,
                                                             
                                                             ymin      = 0,
                                                             ylab      = 'Total Accepted Nominations',
                                                             xlab      = '',
                                                             wrap_scale = "free",
                                                             facet_cols = 1,
                                                             facet_rows = 1)
  
  mayor.councils.count 
  
} else {
  print('No Confirmed Mayor Nominations, try again later :]')
}


message('All Rmd code run for How to Vote data')

```

