---
title: 'How to Vote'
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    self_contained: false
---


<style>

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 115px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
height: 100%;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

.leaflet-control-attribution{
display:none;
}

.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table {
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}


</style>


<!-- set global options here? -->
```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, warning = FALSE, fig.fullwidth = TRUE)
library(ggplot2)

```



Headlines
==============================================================


Column {data-width = 300}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates once a day at 8am.
</br> Last update: **`r Sys.time()`**
</br>
</br>


```{r}

How_to_Vote_Headline

```


Column {data-width = 600}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**


```{r, fig.width=10, fig.height=5, fig.align = 'center'}

if(file_list >= 5) {
  
  htv_status_plot <- ggplot(data = Materials_status_date,
                            mapping = aes(x = DateLodged, y = NumberOfItems, fill = Status)) +
    
    geom_bar(stat = "identity") +
    labs(title = paste("Status of how to vote material by lodgement date (up to " , 
                       format(Sys.Date(), format="%d-%b-%y"),")", "\n", sep = ""),
         x = "\nDate lodged",
         y = "Total number of items\n\n") +
    
    scale_x_date(labels = date_format("%a %d %b"), date_breaks = "1 day") +
    scale_y_continuous(breaks = pretty_breaks()) +
    scale_fill_brewer(palette="RdYlBu", name = "HTV Status", direction = -1) +
    
    ## Create the themes
    theme(axis.title.x     = element_text(face   = "bold", colour = "black", size = 10),
          axis.text.x      = element_text(angle  = 45, hjust = 1),
          axis.title.y     = element_text(face   = "bold", 
                                          colour = "black", 
                                          size   = 10),
          legend.title     = element_text(face   = "bold"),
          
          panel.background = element_rect(fill   = "azure2",
                                          colour = "azure2",
                                          size   = 0.5, linetype = "solid"),
          panel.grid.major = element_line(size   = 0.5, linetype = 'solid',
                                          colour = "white"), 
          panel.grid.minor = element_blank())
  
  htv_status_plot
  
} else {
  message('No data for graph, create message instead of plot')
}

```



<!-- Counts of Material by Date -->
<!-- ============================================================================== -->


<!-- Column -->
<!-- ------------------------------------- -->


<!-- ```{r Markoffs-data_n_chart, fig.width=15, fig.height=10, fig.align='center'} -->

<!-- ## -->
<!-- if(nrow(KPI_HTV_group_date) > 3)  { -->

<!--   HTV.cumul.linplot <- ggplot(KPI_HTV_group_date %>% -->
<!--                                         mutate(LastLabel = ifelse(Date == max(Date), Lodg_cum_count, NA)),  -->
<!--                                       aes(x      = Date,  -->
<!--                                           y      = Lodg_cum_count, -->
<!--                                           colour = Status)) + -->
<!--     geom_line(size = 3) + -->
<!--     facet_wrap(vars(Status), -->
<!--                nrow = 3, ncol = 3, scales = 'free') + -->
<!--     geom_point(size = 5, colour = 'grey') + -->

<!--     theme_light(base_size = 16) + -->
<!--     ylab("Material Count") + -->
<!--     labs(title = "Cumulative How To Vote Material") + -->

<!--     geom_text(aes(label = LastLabel, -->
<!--                   vjust = 2), -->
<!--               size = 5) + -->

<!--     scale_x_date(date_labels = "%b-%d", date_breaks = "2 day") + -->

<!--     theme(plot.margin      = unit(c(1, 1, 1, 1), "cm"), -->
<!--           plot.title       = element_text(vjust  = 5,        size  = 25,     face  = "bold"), -->
<!--           axis.text.x      = element_text(size   = 15,       angle = 45,     hjust = 1, vjust = 1), -->
<!--           axis.title.x     = element_text(size   = 20,       face  = "bold", vjust = -5), -->
<!--           axis.line        = element_line(colour = 'black',  size  = 0), -->
<!--           strip.text       = element_text(size   = 15,       face  = 'bold', colour = 'black'), -->
<!--           strip.background = element_rect(color  = "black",  fill  = "white"), -->
<!--           legend.position  = 'none', -->

<!--           axis.title.y  = element_text(size = 20,  face = "bold", vjust = 4), -->
<!--           axis.text.y   = element_text(size = 15), -->
<!--           plot.subtitle = element_text(size = 20, hjust = 0.5, face = "italic", color = "black"), -->
<!--           plot.caption  = element_text(size = 20, hjust = 0.5, face = "italic", color = "black")) -->

<!--   HTV.cumul.linplot -->

<!-- } else { -->
<!--   message('No data for graph, create message instead of plot') -->
<!--   HTV.cumul.linplot <- 'Insufficient data for graph, try again later :]' -->
<!--   HTV.cumul.linplot -->
<!-- } -->

<!-- ``` -->


<!-- **This graph displays the total How To Vote (HTV) Material by status.** -->
<!-- Status Definitions. -->
<!-- **Accepted:** HTV Material Accepted -->
<!-- **Withrdrawn:** HTV Material withdrawn by Candidate \ -->
<!-- **Rejected:** HTV Material Rejected -->
<!-- **Processing:** HTV Material the NSWEC processing team for review -->




Counts of Material
=====================================


Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**


```{r, fig.width=10, fig.height=6, fig.align = 'center'}

if(file_list >= 5) {
  htv.material.count  <- dash_bar_chart_xvar(df        = Total_pieces_material,
                                             
                                             # title     = '',
                                             
                                             paste("Total Pieces of How-to-Vote material by Type (up to " ,
                                                   format(Sys.Date(), format = "%d-%b-%y"),")", "\n", sep = ""),
                                             caption   = '',
                                             
                                             xvar      = 'Material Type',
                                             yvar      = 'Total pieces of material',
                                             ordervar  = 'Material Type',
                                             
                                             colours   =  c('Mayor'       = "#1B9E77", 
                                                            'Councillor'  = "#1B9E77", 
                                                            'Referendum'  = "#1B9E77", 
                                                            'Poll'        = "#1B9E77",
                                                            'Other'       = "#7570B3"), 
                                             
                                             tsize     = 15,
                                             capt_size = 15,
                                             xsize     = 15,
                                             ysize     = 15,
                                             ycol      = 'black',
                                             lab_size  = 5,
                                             leg_pos   = 'none',
                                             axis_size = 1,
                                             h_just    = -0.3,
                                             
                                             ymin      = 0,
                                             ymax      = max(Total_pieces_material$`Total pieces of material`) +
                                               (max(Total_pieces_material$`Total pieces of material`))*0.2,
                                             ylab      = '',
                                             xlab      = '', 
                                             mar       = 1,
                                             pan_mar   = 0.5)
  
  htv.material.count
  
} else {
  message('No data for graph, create message instead of plot')
  # print('Insufficient data for graph, try again later :]')
}

```




```{r, fig.width=12, fig.align = 'center'}

if(file_list >= 5) {
  htv.councils.count  <- dash_bar_chart_yvar_samecol_lab_facet(df        = Total_pieces_material_council,
                                                               title     = paste("Total Pieces of How-to-Vote material by Council"),
                                                               caption   = '',
                                                               
                                                               xvar      = 'Council Name',
                                                               yvar      = 'Total pieces of material',
                                                               ordervar  = 'Total pieces of material',
                                                               
                                                               group_var = 'Status',
                                                               colour    =  c("deepskyblue"), 
                                                               
                                                               tsize     = 20,
                                                               capt_size = 15,
                                                               xsize     = 15,
                                                               ysize     = 15,
                                                               ycol      = 'black',
                                                               lab_size  = 5,
                                                               leg_pos   = 'none',
                                                               axis_size = 1,
                                                               h_just    = -0.3,
                                                               
                                                               mar       = 1,
                                                               pan_mar   = 0.5,
                                                               
                                                               ymin      = 0,
                                                               ymax      = max(Total_pieces_material_council$`Total pieces of material`) +
                                                                 (max(Total_pieces_material_council$`Total pieces of material`))*0.2,
                                                               ylab      = '',
                                                               xlab      = '', 
                                                               wrap_scale = "free",
                                                               facet_cols = 1,
                                                               facet_rows = 1)
  
  htv.councils.count 
  
} else {
  message('No data for graph, create message instead of plot ')
}

```



Counts of Material by RPP
=====================================


### **EventGroupID: ** **`r event_group_ID`**

```{r}

if(file_list >= 5) {
  
  DT::datatable(Total_material_by_RPP_candidates %>% 
                  rename(`Party Name` = PARTYNAME,
                         `Abbreviated Party Name` = PARTYABBREVIATEDNAME), #%>% 
                #filter(`Total pieces of material expected` > 0), 
                
                rownames   = FALSE, 
                extensions = 'Buttons', 
                filter     = 'top',
                
                options = list(
                  pageLength = 50
                  ,dom = 'tip'
                  ,scrollY = '100%'
                  ))
  
  
} else {
  message('No data for graph, create message instead of plot')
}

```





Applications by Candidates
=====================================


Column {data-width = 800}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**

```{r}

## Arrange the table by the contests with shortfalls - i.e. positive numbers
if(file_list >= 5) {
  
  DT::datatable(Candidates_material %>% arrange(-desc(`Total pieces of material`), 
                                                desc(`Represent a Group`), `Last Name`), #Candidates_not_submitted, 
                
                rownames   = FALSE, 
                extensions = 'Buttons', 
                filter     = 'top',
                
                options = list(
                  pageLength = 50
                  ,dom = 'tip'
                  ,scrollY = '100%'
                  ))
  
  
} else {
  message('No data for table, create message instead of plot')
  # print('Insufficient data for table, try again later :]')
}

```


Column {data-width = 300}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**


```{r, fig.width=7,  fig.height=4, fig.align = 'center'}


if(file_list >= 5) {
  htv.material.count  <- dash_bar_chart_xvar(df        = Total_material_by_RPP_count,

                                             title     = paste("Total Candidate Submissions (up to " ,
                                                               format(Sys.Date(), format = "%d-%b-%y"),")", "\n", sep = ""),
                                             caption   = '',

                                             xvar      = 'Candidates',
                                             yvar      = 'Applications by candidates',
                                             ordervar  = 'Applications by candidates',

                                             colours   =  c('Submitted Candidates'    = "#1B9E77",
                                                            'Un-submitted Candidates' = "#7570B3"),

                                             tsize     = 10,
                                             capt_size = 10,
                                             xsize     = 10,
                                             ysize     = 10,
                                             ycol      = 'black',
                                             lab_size  = 5,
                                             leg_pos   = 'none',
                                             axis_size = 1,
                                             h_just    = -0.3,

                                             ymin      = 0,
                                             ymax      = max(Total_material_by_RPP_count$`Applications by candidates`) +
                                               (max(Total_material_by_RPP_count$`Applications by candidates`))*0.2,
                                             ylab      = '',
                                             xlab      = '',
                                             mar       = 1,
                                             pan_mar   = 0.5)

  htv.material.count

} else {
  message('No data for graph, create message instead of plot ')
  # print('Insufficient data for table, try again later :]')
}

##
message('All RMD code run for How to Vote data')


```



