---
title: 'BallotTrack'
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    self_contained: false
---


<style>

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 115px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
height: 100%;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table {
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container { 
background: #0184a9;
}

<!-- .highcharts-axis-labels highcharts-xaxis-labels{ -->
<!-- font-size:100px; -->
<!-- } -->

</style>


<!-- set global options here? -->
```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, warning = FALSE, fig.fullwidth = TRUE)
library(ggplot2)

```


Overall Scan Progress 
==============================================================


Column {data-width = 1}
-----------------------------------------------------------------------


\
\
\

Column {data-width = 5}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
<!-- </br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm. -->
<!-- </br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `** -->



```{r, fig.width=30, fig.height=15, fig.align = 'center'}

my_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <-  c('#d3d3d3', '#50C878')


## The overall graph
if(nrow(ballot_track_overall_progress) > 0) {
  
  ## Stacked + percent - scan out
  BT_progress <- hchart(ballot_track_overall_progress, type = 'bar', 
                        hcaes( y = Percent, group = Scanned, x = Status)) %>%
    
    hc_title(
      text = "<b>Overall Ballot Track Scanning Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      title    = list(
        text   = "Percent",       # The actual title text
        align  = "high",          # Documentation says options are: low, middle or high
        margin = 10,              # Number of pixels between the title and the axis line
        
        style        = list(
          fontWeight = "bold",    # Bold
          fontSize   = '100px',   # 1.4 x tthe size of the default text
          color      = "#000000"  # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text  = ""),
      alternateGridColor = "#FDFFD5",
      opposite   = FALSE,
      margin     = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 60)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)        %>% 
    hc_size(height = 650)
  
  BT_progress
  
} else {
  print('No Cartons have bee scanned, try again later :]')
}

```

<!-- </br> **For each Ballot track scanning status, these graphs display the % of all Cartons which have been**  -->
<!-- </br> **completely processed through that staus (i.e. all Cartons have been scanned in or out) for each RO**.  -->
<!-- </br> **RO count includes Newcastle and Sydney Count Centres, and the CPVC.** -->


Column {data-width = 1}
-----------------------------------------------------------------------


\
\
\


RO Scan Progress
==============================================================



Column {data-width = 5}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>


```{r, fig.width=20, fig.height=6, fig.align = 'center'}
if(nrow(RO_2.0_percent_scanned_graph) > 0) {
  
  ## Phase 2
  BT_2.0_progress <- hchart(RO_2.0_percent_scanned_graph, type = 'bar', 
                            hcaes( y = Percent, group = Scanned, x = `RO Name`)) %>%
    
    hc_title(
      text   = "<b>RO Scan-in from Printer Progress<b>",
      margin = 40,
      align  = "left",
      style  = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",        # The actual title text
        align = "high",          # Documentation says options are: low, middle or high
        margin = 10,             # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',   # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)        %>% 
    hc_size(height = 1500)
  
  
  
  ## Phase 3 :
  BT_3.0_progress <- hchart(RO_3.0_percent_scanned_graph, type = 'bar', 
                            hcaes( y = Percent, group = Scanned, x = `RO Name`)) %>%
    
    hc_title(
      text   = "<b>RO Scan-out to Venue Progress<b>",
      margin = 40,
      align  = "left",
      style  = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",       # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',   # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  
  ## Phase 4
  BT_4.0_progress <- hchart(RO_4.0_percent_scanned_graph, type = 'bar',
                            hcaes( y = Percent, group = Scanned, x = `RO Name`)) %>%
    
    hc_title(
      text = "<b>RO Scan-in from Venue Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",       # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  
  ## Phase 5.10
  BT_5.10_progress <- hchart(RO_5.10_percent_scanned_graph, type = 'bar',
                             hcaes( y = Percent, group = Scanned, x = `RO Name`)) %>%
    
    hc_title(
      text = "<b>RO scan-out to CC Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",    # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',    # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  
  ## Phase 5.11
  BT_5.11_progress <- hchart(RO_5.11_percent_scanned_graph, type = 'bar',
                             hcaes( y = Percent, group = Scanned, x = `Count Centre Name`)) %>%
    
    hc_title(
      text = "<b>Count Centre Scan-in from RO Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",    # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',    # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  ## Phase 5.0
  BT_5.0_progress <- hchart(RO_5.0_percent_scanned_graph, type = 'bar',
                            hcaes( y = Percent, group = Scanned, x = `RO Name`)) %>%
    
    hc_title(
      text = "<b>RO Scan-out to Warehouse Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",    # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',    # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  
  ## Phase 5.14
  BT_5.14_progress <- hchart(RO_5.14_percent_scanned_graph, type = 'bar',
                             hcaes( y = Percent, group = Scanned, x = `Count Centre Name`)) %>%
    
    hc_title(
      text = "<b>Count Centre Scan in to ULD Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin = 40,
      maxPadding = 30,
      title = list(
        text = "Percent",    # The actual title text
        align = "high",         # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style = list(
          fontWeight = "bold",   # Bold
          fontSize = '10.5em',    # 1.4 x tthe size of the default text
          color = "#000000"      # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>%  
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(my_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1500)
  
  
  ## Panel of all figures
  Ballot_track_grid <- hw_grid(BT_2.0_progress,
                               BT_3.0_progress,
                               BT_4.0_progress,
                               BT_5.10_progress,
                               BT_5.11_progress,
                               BT_5.0_progress, ncol = 2)
  
  Ballot_track_grid
  
} else {
  print('No Cartons have bee scanned, try again later :]')
}

```


\


RO Scan-in from Printer
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of carton scans - Returning Office/STH/CPVC Scan-in from Printer **

```{r}

## View here
datatable(RO_2.0_scan_in_from_printer %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`), 
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_2.0_scan_in_from_printer)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)

```



RO Scan Out to venue
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of carton scans - Returning Office Scan-out to Venue **

```{r}

datatable(RO_3.0_scan_out_to_venue %>%
            
            ## 
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`), 
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_3.0_scan_out_to_venue)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)

```





RO Scan-in from Venue
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of scans - Returning Office Scan-in from Venue **

```{r}

datatable(RO_4.0_scan_in_from_venue %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`),
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_4.0_scan_in_from_venue)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)


```





RO Scan-out to Count Centre
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of scans Returning Office Scan-out to Count Centre **

```{r}

datatable(RO_5.10_scan_out_to_CC %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`),
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_5.10_scan_out_to_CC)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)

```






Count Centre Scan-in from RO
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of scans Count Centre Scan-in from Returning Office **

```{r}

datatable(RO_5.11_scan_from_RO_to_CC %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`),
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_5.11_scan_from_RO_to_CC)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)

```






RO Scan-out to Warehouse 
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of scans - Returning Office Scan-out to Warehouse **

```{r}

datatable(RO_5.0_scan_out_to_Ware %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`,
                    `Contest Name`) %>% ungroup %>% dplyr::select(-ContestType), 
          
          rownames     = FALSE, 
          extensions   = 'Buttons', 
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_5.0_scan_out_to_Ware)), fontSize = "9pt") %>% 
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)


```



Count Centre Scan in to ULD
=====================================


Column {data-width = 800}
-------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> Data is **not** updated in real time. Updates occur every 30 minutes between 8am and 6pm.
</br> Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
</br>

### **Progress of scans - Count Centre Scan Carton into ULD **

```{r}

datatable(RO_5.14_CC_scan_in_to_ULD %>%
            
            ## Sort columns
            arrange(`RO Name`,
                    `ContestType`,
                    `UseCase`,
                    `Container Name`),
          
          rownames     = FALSE,
          extensions   = 'Buttons',
          filter       = 'top',
          
          options      = list(
            pageLength = 100,
            dom        = 'Btip',
            scrollY = '100%',
            buttons    = c('csv', 'excel'))) %>%
  
  formatStyle(columns = rep(1:length(RO_5.14_CC_scan_in_to_ULD)), fontSize = "9pt") %>%
  formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1)

## Final message
message('All BallotTrack RMD code run')

```




