---
title: "RMT Batching"
output: flexdashboard::flex_dashboard
---
<style>

.navbar-inverse .navbar-nav>li>a {

color:#000000;
}


.tab-content {

	padding-top:30px;


}

.container-fluid {
	
	background-color:white;
	padding-bottom:0px;
	
}

.bluebox {
 background-color: #2571bd;
    border: solid #ddd 1px;
    font-size: 15px;
    height:40px;
    padding:5px;
    margin-bottom: 5px;
    border-radius:5px;
	color: #f9f9f9;
	}

body {
    padding:0px;
    padding-top:20px;

 background-color: white;

}

h1 {
    font-size: 25px;
}

.leaflet-control-attribution{
display:none;
}

.leaflet-container {
 background-color: white;


}


.leaflet-popup-content-wrapper {
 background: #eff4ef2e;
 box-shadow:0 3px 10px rgba(0, 0, 0, 0);

}


.gmisc_table {

 width:max-content;


}


.btn {
    background-color: DodgerBlue;
    border: none;
    color: white;
    cursor: pointer;
    font-size: 15px;
}

.btn:hover {
    background-color: #3d6ece;
}

table { 
    border-spacing: 5px;
    border-collapse: separate;
    border:1px
}

.p {
margin-top:20px

}

div.text1 {
border: solid #ddd 1px;
background-color: #f9f9f9;
padding-left:20px;
padding-top:10px;
padding-bottom:10px;
margin-top:20px;
margin-bottom:20px;
border-radius:3px;
}



div.header{

padding-top:30px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
    position: sticky;
    bottom: 0;
    width: 100%;
	height:30px;
    background-color: #2b6eda;
    color: white;
    text-align: center;
}

div.main-wrapper {
    position: relative;
}

<!-- .navbar-fixed-top { -->

<!-- visibility: hidden; -->

<!-- } -->



</style>

Summary
=====================================

Column {data-width=10}
-------------------------------------
### Number of ballot paper counted: 

Councillor
```{r, echo=FALSE, warning=FALSE, message=FALSE}

formattable(Councillor_bp_counted) 

```

Mayor
```{r, echo=FALSE, warning=FALSE, message=FALSE}

formattable(Mayor_bp_counted) 


```  

Ref & Poll
```{r, echo=FALSE, warning=FALSE, message=FALSE}

formattable(Ref_poll_bp_counted)

```

### Place holder for potential display
```{r, echo=FALSE, warning=FALSE, message=FALSE}




```  



Column {data-width=6}
-------------------------------------
### Last updated: **`r Sys.time()`**  with Event Group: **`r event_group_ID`**

<span class="demospan">% of Counts that matched excluding the manually approved  </span>
<div class="expdiv">
<table>
<tr>
<td>

```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(round(nrow(Councillor_show %>% filter(abs(Councillor_show$Diff/Councillor_show$InitialCount) <0.01))/nrow(Councillor_show),2)*100
, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(90, 100)
  ,warning = c(40, 89)
  ,danger = c(0,39)))

```
<span class="demospan">Councillor</span>

</td>

<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(round(nrow(Mayor_show %>% filter(abs(Mayor_show$Diff/Mayor_show$InitialCount) <0.01))/nrow(Mayor_show),2)*100
, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(90, 100)
  ,warning = c(40, 89)
  ,danger = c(0,39)))


#gauge(current_missing_LGA, min = 0, max = nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), symbol = '', gaugeSectors(
#  success = c(0, 0.05*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
#  ,warning = c(0.05001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), 0.2*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
#  ,danger = c(0.2001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))))

```
<span class="demospan">Mayor</span>

</td>
</tr>
</table>

<span class="demospan">% of Counts that matched including the manually approved  </span>
<table>

<tr>
<td>

```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(round(nrow(Councillor_show %>% filter(RequireChecking == 'No'))/nrow(Councillor_show),2)*100
, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(90, 100)
  ,warning = c(40, 89)
  ,danger = c(0,39)))

```
<span class="demospan">Councillor</span>

</td>

<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(round(nrow(Mayor_show %>% filter(RequireChecking == 'No'))/nrow(Mayor_show),2)*100
, min = 0, max = 100, symbol = '%', gaugeSectors(
  success = c(90, 100)
  ,warning = c(40, 89)
  ,danger = c(0,39)))


#gauge(current_missing_LGA, min = 0, max = nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), symbol = '', gaugeSectors(
#  success = c(0, 0.05*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
#  ,warning = c(0.05001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), 0.2*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
#  ,danger = c(0.2001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))))

```
<span class="demospan">Mayor</span>

</td>

</tr>
</table>
</div>

    
### Data sources and Rules
<span class="demospan">
First count data come from EMA and Check count data come from PRCC with the exception that: <br> <p></p>
LG2103 at the moment does not have PRCC info
Ref_poll check count decvote figure is missing at the moment.  <br> <p></p>



Auto checking will put a 'No' in the Require Checking field allowing user to filter and focus on venues that require attention. <br><p></p>
Below are the rules that is applied: <br><p></p>
1: Diff within 1% of initial count  <br>
2: Comment in EMA: accepted by ROSO

</span>

```{r}





```




Councillor
=====================================

Column {data-width=3}
-------------------------------------
### Councillor
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}

datatable(Councillor_show, 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                             searchCols = list(
                              list(search = '["Yes"]')),
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```



Mayor
=====================================

Column {data-width=3}
-------------------------------------
### Mayor
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}


datatable(Mayor_show, 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                            searchCols = list(
                              list(search = '["Yes"]')),
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```


Ref & Poll
=====================================

Column {data-width=3}
-------------------------------------
### Referendum and Poll
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}


datatable(Ref_poll_show, 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                 searchCols = list(
                              list(search = '["Yes"]')),
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```
