---
title: "RMT Pre Poll"
output: flexdashboard::flex_dashboard
---
<style>

.navbar-inverse .navbar-nav>li>a {

color:#000000;
}


.tab-content {

	padding-top:30px;


}

.container-fluid {
	
	background-color:white;
	padding-bottom:0px;
	
}

.bluebox {
 background-color: #2571bd;
    border: solid #ddd 1px;
    font-size: 15px;
    height:40px;
    padding:5px;
    margin-bottom: 5px;
    border-radius:5px;
	color: #f9f9f9;
	}

body {
    padding:0px;
    padding-top:20px;

 background-color: white;

}

h1 {
    font-size: 25px;
}

.leaflet-control-attribution{
display:none;
}

.leaflet-container {
 background-color: white;


}


.leaflet-popup-content-wrapper {
 background: #eff4ef2e;
 box-shadow:0 3px 10px rgba(0, 0, 0, 0);

}


.gmisc_table {

 width:max-content;


}


.btn {
    background-color: DodgerBlue;
    border: none;
    color: white;
    cursor: pointer;
    font-size: 15px;
}

.btn:hover {
    background-color: #3d6ece;
}

table { 
    border-spacing: 5px;
    border-collapse: separate;
    border:1px
}

.p {
margin-top:20px

}

div.text1 {
border: solid #ddd 1px;
background-color: #f9f9f9;
padding-left:20px;
padding-top:10px;
padding-bottom:10px;
margin-top:20px;
margin-bottom:20px;
border-radius:3px;
}



div.header{

padding-top:30px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
    position: sticky;
    bottom: 0;
    width: 100%;
	height:30px;
    background-color: #2b6eda;
    color: white;
    text-align: center;
}

div.main-wrapper {
    position: relative;
}

<!-- .navbar-fixed-top { -->

<!-- visibility: hidden; -->

<!-- } -->



</style>

Current Day
=====================================

Column {data-width=10}
-------------------------------------
### Pre Poll and AoBP. Last updated: **`r Sys.time()`**
```{r, echo=FALSE, warning=FALSE, message=FALSE}


datatable(PrePoll_reconcilliation_allocations %>% ungroup() %>% filter(ReconciliationDate == max(ReconciliationDate)) %>% dplyr::select(-LocationID, -`Pre-poll`, -DecVote, -Spoilt, -Discarded,-ContestID,LocationType,-MarkOffDay, -Quantity, - LocationType, -AreaCode), 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```   


Column {data-width=5}
-------------------------------------
### Current Day AoBP Statuses

<div class="expdiv">
<table>
<tr>
<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(current_missing_PP, min = 0, max = nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)), symbol = '', gaugeSectors(
  success = c(0, 0.05*nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)))
  ,warning = c(0.05001*nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)), 0.20*nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)))
  ,danger = c(0.2001*nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)), nrow(Total_Allocations %>% ungroup() %>% distinct(LocationID)))))

```
<span class="demospan">AoBP not yet completed - Pre polling places</span>
</td>

<td>
```{r, echo=FALSE, warning=FALSE, message=FALSE}

gauge(current_missing_LGA, min = 0, max = nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), symbol = '', gaugeSectors(
  success = c(0, 0.05*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
  ,warning = c(0.05001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), 0.2*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))
  ,danger = c(0.2001*nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)), nrow(Total_Allocations %>% ungroup() %>% distinct(AreaCode)))))

```
<span class="demospan">AoBP not yet completed - LGA</span>
</td>
</tr>
</table>
</div>

    
### Pre poll markoff

```{r}


hchart(Daily_prepoll, "line", hcaes(x=DAY, y=Prepoll)) %>%
  hc_title(text = "Pre poll Markoffs")


```




Missing AoBP
=====================================

Column {data-width=3}
-------------------------------------
### Applicant Training Status Election Day
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}

datatable(missing_AoBP %>% ungroup() %>% dplyr::select(-LocationID,-LocationType), 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```



Daily ledger
=====================================

Column {data-width=3}
-------------------------------------
### Applicant Training Status Election Day
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}


datatable(PrePoll_reconcilliation_allocations %>% ungroup() %>% dplyr::select(-LocationID, -`CumulativePre-poll`, -CumulativeDecVote, -CumulativeSpoilt, -CumulativeDiscarded,-Q_M_S,-LocationType), 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```


Daily ledger Cumulative
=====================================

Column {data-width=3}
-------------------------------------
### Applicant Training Status Election Day
```{r, fig.width=18, echo=FALSE, warning=FALSE, message=FALSE}


datatable(PrePoll_reconcilliation_allocations %>% ungroup() %>% dplyr::select(-LocationID, -`Pre-poll`, -DecVote, -Spoilt, -Discarded,-LocationType), 
              rownames= FALSE, extensions = 'Buttons',filter = 'top',
              options = list(
                            dom = 'Blfrtip',
                             pageLength = 10,
                             lengthMenu = c(10, 25, 50)),
                              height = '480px',
                              width='650px')



```
