---
title: " Count centres "
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    self_contained: true
---


<style>

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 115px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
height: 100%;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table {
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container { 
background: #0184a9;
}


</style>





```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, warning = FALSE, fig.fullwidth = TRUE)
library(ggplot2)

```


Overall Count Centre Progress
=========================================


Column {data-width = 400}
-----------------------------------------------------------------------


### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at the Sydney and Newcastle Count Centres, and doesn't include postal
</br> Data is **not** updated in real time. Count Centre data are refreshed after each execution of the Count Centre 
</br> Management Tool. RO data are refreshed every 15mins. The page reloads data every 15mins. Be sure to hit 'Refresh'
</br> for latest available information. Last page reload: **`r Sys.time()`**
</br> 
</br>


```{r Syd Headline Table, width = 300}

Syd_Centre_HeadlineTable

```


```{r Newcastle Headline Table}

Newcastle_Count_HeadlineTable

```



Column {data-width = 400}
-----------------------------------------------------------------------


### **Count Centre Progress Graphs**
</br> These graphs display the percent complete for each counting process (batching and data Entry) at each Count Centre.
</br> **Elapsed time** is calculated as the elapsed number of working days (i.e. excluding Sundays) divided by the total number 
</br> of working days in the entire counting period (i.e. as a percentate of available time elapsed). Elapsed time maxes out 
</br> at 100%.
</br> 
</br>

```{r, fig.width=6.5, fig.height=4, fig.align = 'center'}

## 
batch_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <-  c('#d3d3d3', '#ff7f50')

## 
if(nrow(Syd_percent_remaining) > 0) {
  
  ## Stacked + percent - scan out
  Syd_count_centre_batch_progress <- hchart(Syd_percent_remaining_batch, 
                                            type       = 'bar',
                                            pointWidth = 50,
                                            
                                            hcaes(y     = Proportion, 
                                                  group = Progress, 
                                                  x     = Status)) %>%
    
    hc_title(
      text = "<b>Sydney : Batching Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = syd_batching_elapsed_prop,
        color = 'blue',
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 10)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(width = 1000, height = 400)
  
  ## Data theme
  data_theme <- hc_theme(
    chart = list(
      backgroundColor = 'transparent', 
      style = list(
        fontFamily = "Helvetica")))
  cols <-  c('#d3d3d3', '#50C878')
  
  ## Stacked + percent - scan out
  Syd_count_centre_data_progress <- hchart(Syd_percent_remaining_data, 
                                           type       = 'bar',
                                           pointWidth = 50,
                                           
                                           hcaes(y     = Proportion, 
                                                 group = Progress, 
                                                 x     = Status)) %>%
    
    hc_title(
      text = "<b>Sydney : Data Entry Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = syd_data_entry_elapsed_prop,
        color = "blue",
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 10)) %>%
    
    ## Need this to make the graphs the same
    hc_add_theme(data_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(width = 1000, height = 400)
  
  
  ## Panel of both figures
  Syd_overall_count_grid <- hw_grid(Syd_count_centre_batch_progress,
                                    Syd_count_centre_data_progress, 
                                    ncol = 2)
  
  Syd_overall_count_grid
  
} else {
  print('No Sydney Counting data, try again later :]')
}

```

</br> 
</br>


```{r, fig.width=25, fig.height=4, fig.align = 'center'}

## 
batch_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <-  c('#d3d3d3', '#ff7f50')


## 
if(nrow(Newcastle_percent_remaining) > 0) {
  
  ## Stacked + percent - scan out
  newc_count_centre_batch_progress <- hchart(newc_percent_remaining_batch, 
                                             type       = 'bar',
                                             pointWidth = 50,
                                             
                                             hcaes(y     = Proportion, 
                                                   group = Progress, 
                                                   x     = Status)) %>%
    
    hc_title(
      text = "<b>Newcastle : Batching Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = newc_batching_elapsed_prop,
        color = 'blue',
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 10)) %>%
    hc_add_theme(data_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(width = 1000, height = 400)
  
  ## Data theme
  data_theme <- hc_theme(
    chart = list(
      backgroundColor = "transparent", 
      style = list(
        fontFamily = "Helvetica")))
  cols <-  c('#d3d3d3', '#50C878')
  
  ## Stacked + percent - scan out
  newc_count_centre_data_progress <- hchart(newc_percent_remaining_data, 
                                            type       = 'bar',
                                            pointWidth = 50,
                                            
                                            hcaes(y     = Proportion, 
                                                  group = Progress, 
                                                  x     = Status)) %>%
    
    hc_title(
      text = "<b>Newcastle : Data Entry Progress<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = newc_data_entry_elapsed_prop,
        color = 'blue',
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 10)) %>%
    hc_add_theme(data_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(width = 1000, height = 400)
  
  ## Panel of both figures
  newc_overall_count_grid <- hw_grid(newc_count_centre_batch_progress,
                                     newc_count_centre_data_progress, 
                                     ncol = 2)
  
  newc_overall_count_grid
  
} else {
  print('No Newcastle Counting data, try again later :]')
}

```


Progress by Contest : Sydney
=========================================



Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at Sydney Count Centre, and does not include Newcastle Count Centre, Postal and RO Offices.
</br> **Elapsed time** is calculated as the elapsed number of working days (i.e. excluding Sundays) divided by the total number 
</br> of working days in the entire counting period (i.e. as a percentate of available time elapsed). It maxes out at 100%.
</br> Data is **not** updated in real time. The page reloads data from the Count Centre Management Tool every 15mins. 
</br> Last page reload: **`r Sys.time()`**
</br>
</br>



```{r, fig.width=25, fig.align = 'center'}


batch_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <-  c('#d3d3d3', '#ff7f50')


if(nrow(syd_contest_percent_remaining) > 0) {
  
  ## Contest batching progress
  Syd_Contest_Batching_Progress <- hchart(syd_contest_batch_percent_remaining, 
                                          type        = 'bar', 
                                          hcaes(y     = Proportion, 
                                                group = Progress, 
                                                x     = Contest)) %>%
    
    hc_title(
      text = "<b>Sydney : Batching Progress by Contest<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value  = syd_batching_elapsed_prop,
        color  = 'blue',
        width  = 3,
        zIndex = 4,
        label  = list(text = "Elapsed Time",
                      style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title    = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize   = '10.5em',  # 1.4 x tthe size of the default text
          color      = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text  = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30) %>% 
    
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(height = 2000)
  
  
  
  
  data_theme <- hc_theme(
    
    chart = list(
      backgroundColor = "transparent", 
      style = list(
        fontFamily = "Helvetica")))
  cols <-  c('#d3d3d3', '#50C878')
  
  ## Contest batching progress
  Syd_Contest_Data_Progress <- hchart(syd_contest_data_percent_remaining, 
                                      type        = 'bar', 
                                      hcaes(y     = Proportion, 
                                            group = Progress, 
                                            x     = Contest)) %>%
    
    hc_title(
      text = "<b>Sydney : Data Entry Progress by Contest<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value   = syd_data_entry_elapsed_prop,
        color   = 'blue',
        width   = 3,
        zIndex  = 4,
        label   = list(text = "Elapsed Time",
                       style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>%
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ##  Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(height = 2000)
  
  
  ## Panel of both figures
  Syd_contest_count_grid <- hw_grid(Syd_Contest_Batching_Progress,
                                    Syd_Contest_Data_Progress, 
                                    ncol = 2)
  
  Syd_contest_count_grid
  
  
} else {
  print('No counting data has been entered for Sydney, try again later :]')
}


```



Progress by Contest : Newcastle
=========================================



Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at Newcastle Count Centre, and does not include Sydney Count Centre, Postal and RO Offices.
</br> **Elapsed time** is calculated as the elapsed number of working days (i.e. excluding Sundays) divided by the total number 
</br> of working days in the entire counting period (i.e. as a percentate of available time elapsed). It maxes out at 100%.
</br> Data is **not** updated in real time. The page reloads data from the Count Centre Management Tool every 15mins. 
</br> Last page reload: **`r Sys.time()`**
</br> 
</br>



```{r, fig.width=25, fig.height=8, fig.align = 'center'}

batch_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <-  c('#d3d3d3', '#ff7f50')


if(nrow(newc_contest_percent_remaining) > 0) {
  
  ## Contest batching progress
  Newc_Contest_Batching_Progress <- hchart(newc_contest_batch_percent_remaining, 
                                           type        = 'bar', 
                                           hcaes(y     = Proportion, 
                                                 group = Progress, 
                                                 x     = Contest)) %>%
    
    hc_title(
      text = "<b>Newcastle : Batching Progress by Contest<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value   = newc_batching_elapsed_prop,
        color   = 'blue',
        width   = 3,
        zIndex  = 4,
        label   = list(text = "Elapsed Time",
                       style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>%
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ##  Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(height = 600)
  
  
  data_theme <- hc_theme(
    chart = list(
      backgroundColor = "transparent", 
      style = list(
        fontFamily = "Helvetica")))
  cols <-  c('#d3d3d3', '#50C878')
  
  ## Contest batching progress
  Newc_Contest_Data_Progress <- hchart(newc_contest_data_percent_remaining, 
                                       type        = 'bar', 
                                       hcaes(y     = Proportion, 
                                             group = Progress, 
                                             x     = Contest)) %>%
    
    hc_title(
      text   = "<b>Newcastle : Data Entry Progress by Contest<b>",
      margin = 40,
      align  = "left",
      style  = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value   = newc_data_entry_elapsed_prop,
        color   = 'blue',
        width   = 3,
        zIndex  = 4,
        label   = list(text = "Elapsed Time",
                       style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>%
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite   = FALSE,
      margin     = 40,
      maxPadding = 30
    ) %>% 
    
    ##  Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(height = 600)
  
  
  ## Panel of both figures
  Newc_contest_count_grid <- hw_grid(Newc_Contest_Batching_Progress,
                                     Newc_Contest_Data_Progress, 
                                     ncol = 2)
  
  Newc_contest_count_grid
  
  
} else {
  print('No counting data has been entered for Newcastle, try again later :]')
}


```




Contest Completion Forecasts
=========================================


Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at Count Centres, and does not include Postal and RO Offices.
</br> Data is **not** updated in real time. The page reloads data from the Count Centre Management Tool every 15mins. 
</br> Last page reload: **`r Sys.time()`**


### Contest Summary 
```{r echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE, comment = NA, out.width == "100%"}
datatable(forecastSummaryByContest %>% select(-EventGroupID, -Team, 
                                              -BatchingBPsOverCapacity, 
                                              -DataEntryBPsOverCapacity) %>% 
            rename(ReadyForR1 = Batched),
          
          rownames      = FALSE, 
          extensions    = 'Buttons', 
          filter        = 'top',
          
          options       = list(
            pageLength  = 15
            ,dom        = 'Btip'
            ,buttons     = c('csv')
            ,lengthMenu = c(10, 20, 50, 100)
            ,scrollY = 'true'
            # ,scrollX = 'false'
          ))

```


RO Progress Graphs
=====================================


Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at RO Offices, and does not include postal and count centres.
</br> **Elapsed time** is calculated as the elapsed number of working days (i.e. excluding Sundays) divided by the total number 
</br> of working days in the entire counting period (i.e. as a percentate of available time elapsed). It maxes out at 100%.
</br> Data is **not** updated in real time. The page reloads data from the Count Centre Management Tool every 15mins. 
</br> Last page reload: **`r Sys.time()`**
</br> 
</br>



```{r, fig.width=25, fig.height=8, fig.align = 'center'}


batch_theme <- hc_theme(
  chart = list(
    backgroundColor = "transparent", 
    style = list(
      fontFamily = "Helvetica")))
cols <- c('#d3d3d3', '#ff7f50')


if(nrow(RO_count_centre_batch_percent_remaining) > 0) {
  
  ## Contest batching progress
  RO_Count_Centre_Batching_Progress <- hchart(RO_count_centre_batch_percent_remaining, 
                                              type        = 'bar', 
                                              hcaes(y     = Proportion, 
                                                    group = Progress, 
                                                    x     = CountLocation)) %>%
    
    hc_title(
      text = "<b>Batching Progress by Returning Office Count Centre<b>",
      margin = 40,
      align = "left",
      style = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = RO_batching_elapsed_prop,
        color = 'blue',
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>% 
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ##  Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols) %>% 
    hc_size(height = 1000)
  
  
  data_theme <- hc_theme(
    chart = list(
      backgroundColor = "transparent", 
      style = list(
        fontFamily = "Helvetica")))
  cols <-  c('#d3d3d3', '#50C878')
  
  ## Contest batching progress
  RO_Count_Centre_Data_Progress <- hchart(RO_count_centre_data_percent_remaining, 
                                          type        = 'bar', 
                                          hcaes(y     = Proportion, 
                                                group = Progress, 
                                                x     = CountLocation)) %>%
    
    hc_title(
      text   = "<b>Data Entry Progress by Returning Office Count Centre<b>",
      margin = 40,
      align  = "left",
      style  = list(color = "#000000", useHTML = TRUE)) %>% 
    
    hc_yAxis(
      min   = 0, max = 100,
      title = list(text = "<b>Percent (%)<b>"),
      fontWeight = "bold",
      margin     = 40,
      maxPadding = 30,
      
      plotLines = list(list(
        value = RO_data_entry_elapsed_prop,
        color = 'blue',
        width = 3,
        zIndex = 4,
        label = list(text = "Elapsed Time",
                     style = list( color = 'blue', fontWeight = 'bold' )))),
      
      title = list(
        text   = "Percent",     # The actual title text
        align  = "high",        # Documentation says options are: low, middle or high
        margin = 10,            # Number of pixels between the title and the axis line
        style  = list(
          fontWeight = "bold",  # Bold
          fontSize = '10.5em',  # 1.4 x tthe size of the default text
          color = "#000000"     # Hex code for the default blue
        ))) %>%
    
    hc_xAxis(
      title = list(text = ""),
      alternateGridColor = "#FDFFD5",
      opposite = FALSE,
      margin = 40,
      maxPadding = 30
    ) %>% 
    
    ## Make sure the graph is long enough
    hc_plotOptions(series  = list(stacking      = "normal"),
                   bar     = list(pointWidth    = 20)) %>%
    
    hc_add_theme(batch_theme) %>% 
    hc_colors(cols)           %>% 
    hc_size(height = 1000)
  
  
  ## Panel of both figures
  RO_Count_Centre_count_grid <- hw_grid(RO_Count_Centre_Batching_Progress,
                                        RO_Count_Centre_Data_Progress, 
                                        ncol = 2)
  
  RO_Count_Centre_count_grid
  
  
} else {
  print('No counting data has been entered for Sydney, try again later :] ')
}


```




RO Progress Data
=====================================


Column {data-width = 1000}
-----------------------------------------------------------------------

### **EventGroupID: ** **`r event_group_ID`**
</br> The data only represents work occurring at RO Offices, and does not include postal and count centres.
</br> Data is **not** updated in real time. The page reloads data from the Count Centre Management Tool every 15mins. 
</br> Last page reload: **`r Sys.time()`**



### Contest Summary 
```{r echo = FALSE, message = FALSE, warning = FALSE, paged.print = FALSE, comment = NA}
datatable(RO_progress_data %>% rename(ReadyForR1 = Batched) %>% 
            
            filter(CountLocation != "Sydney Count Centre" & CountLocation != "Newcastle Count Centre") %>% 
            select(-EventGroupID, -DataEntryWorkload, -TotalBPsDataEntered, -BPsRemainingForDE),
          
          rownames   = FALSE, 
          extensions = 'Buttons', 
          filter     = 'top',
          
          options       = list(
            pageLength  = 15
            ,dom        = 'Btip',
            buttons     = c('csv')
            ,lengthMenu = c(10, 20, 50, 100)
            ,scrollY = 'true'
            # ,scrollX = 'false'
          ))

```




Counting Definitions
=====================================

Column {data-width = 1}
-----------------------------------------------------------------------

\
\
\

Column {data-width = 2}
-----------------------------------------------------------------------

\

#### **Batching Workload** 
This total is initially the sum of the base data projections for the venues/vote 
types (excluding Postal and iVote). Each projection has its contingency inflation 
removed to ensure the total BPs is in line with expected turnout. As each venue/vote 
type’s Initial Count total becomes available, the Initial Count total replaces the 
base data projection. 

\

#### **Total BPs Batched** 
The number of ballot papers that have been *registered and approved* in PRCC. 

\

#### **BPs Remaining For Batching** 
The number of ballot papers that are *yet to be registered and approved* in PRCC. 
This total is derived by subtracting the ‘Total BPs Batched’ from the ‘Batching Workload’.

\

#### **Scheduled Batching Finish Day** 
The date batching was scheduled to complete in the plan. This date does not change on the display.

\

#### **Projected Batching Finish Day** 
The date batching is now projected to complete according to the count centre operations 
management tool forecast.

\

#### **Elapsed Time** 

'Elapsed time' is calculated as the elapsed number of working days (i.e. excluding Sundays)  
divided by the total number of working days in the entire counting period (i.e. as a percentate  
of available time elapsed). Elapsed time maxes out at 100%. 

\

#### **Data entry Workload** 
The number of ballot papers (ie Batching Workload) to be data entered multiplied by two 
(to represent the two rounds of data entry).

\

#### **Total Data Entered** 
The number of ballot papers that have completed Round 1 of data entry in PRCC plus the 
number of ballot papers that have completed Round 2 of data entry (ie a ballot paper that 
has completed Round 2 will be counted twice).

\

#### **Total Remaining For Data Entry** 
The Data Entry Workload less the Total Data Entered.

\

#### **Scheduled Data Entry Finish Day** 
The date data entry is now projected to complete according to the count centre operations management tool forecast.

\

#### **Contest Completion Forecasts** 
TotalBPsBatched is the total of ReadyForR1, R1_Finished, R2_Finished, Reconciled
In the ‘Day’ columns, day 1 is the first Monday after election day, and day number 
ascends by 1 for each subsequent operational day.

\

Column {data-width = 2}
-----------------------------------------------------------------------

\
\
\




