---
title: "DecVoting"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    self_contained: false
---


<style> 

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 90px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table { 
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>


```{r setup, include = FALSE}
library(ggplot2)
library(RColorBrewer)
library(scales)
library(ggrepel)

```


Enrolment/NAMAV Headlines
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------


### Last update: **`r Sys.time()`** by: **`r if (nchar(Sys.getenv("knit_by")) > 0) {Sys.getenv("knit_by")} else {} `**
Data is **not** updated in real time. Updates occur every 2 hours between 8am and 6pm. 


```{r DecHeadlineTable}

if (Dec_Votes_Available){
  DecHeadlineTable
} else {
  print("No Data Available")
}
```


Column {data-width = 500}
------------------------------------------------------------------------

<!-- Here we have added a barplot for good measure, may not be needed -->


```{r HeadlineDecvote, fig.width=10, fig.align='center'}
if(Dec_Votes_Available) {
  
  ## Create plot
  
  
  #need to have dummy data to let the facet wrap work.
  DummyData<-Overall_DecVote_Chart_Table %>%
    
    filter(Venue_type   == "Polling Place"|
             Venue_type == "Pre-Poll") %>%
    dplyr::select(Venue_type:Total_markoffs)  %>%
    
    group_by(Vote_type) %>%
    mutate(Total_markoffs = ifelse(Total_markoffs == max(Total_markoffs),
                                   Total_markoffs*1.1,Total_markoffs))
  
  
  decvotes.barplot<-ggplot(data = Overall_DecVote_Chart_Table %>%
                             filter(Venue_type   == "Polling Place"|
                                      Venue_type == "Pre-Poll"),
                           
                           aes(x    = reorder(Venue_type, Total_markoffs),
                               y    = Total_markoffs,
                               fill = Venue_type)) +
    
    #geom_bar(stat = "identity") +
    geom_col(position = "dodge") +
    
    coord_flip() +
    scale_fill_manual(values = c('Polling Place' = "deepskyblue", 
                                 'Pre-Poll'      = "coral"), na.value = "grey") +
    scale_x_discrete(drop = FALSE) +
    
    geom_text(aes(label = Total_markoffs, hjust = -0.5,),
              position  = position_dodge(width = 1),
              inherit.aes = TRUE,
              size      = 4) +
    
    theme_classic(base_size = 16) +
    ylab('Declaration Votes')+
    facet_wrap(vars(Vote_type),
               nrow=2,ncol=1,scales='free')+
    
    theme(plot.title      = element_text(vjust = 5, size = 15, face = "bold"),
          plot.margin     = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
          strip.text      = element_text(size  = 15, face = 'bold'),
          
          axis.text.x     = element_text(size = 10),
          axis.title.x    = element_text(size = 10, face = "bold", vjust=-5),
          legend.position = 'top',
          legend.title    = element_blank(),
          legend.text     = element_text(size = 10, color = "black"),
          
          axis.title.y  = element_blank(),
          axis.text.y   = element_text(size = 10, color = "black"),
          plot.subtitle = element_text(size = 10, hjust = 0.5, face = "italic", color = "black"),
          plot.caption  = element_text(size = 10, hjust = 0.5, face = "italic", color = "black"))+
    geom_blank(data=DummyData)
  
  
  
  
  decvotes.barplot
  
} else {
  print("No Data Available")
}


```





Postal Headlines
==============================================================


Column {data-width = 500}
-----------------------------------------------------------------------

Last update: 
**`r Sys.time()`**
Event ID: 
**`r event_group_ID`**

```{r Postal-Headlines, echo = FALSE, fig.width=20}
if (Postal_Votes_Available){
  PostalHeadlineTable
} else {
  print("No Data Available")
}
```


Column {data-width = 500}
-----------------------------------------------------------------------


```{r Postal-headline-chart, fig.align='center', fig.width=10}

if(Postal_Votes_Available) {
  
  
  #need some dummy data for the labels.
  
  Plot_Data <- Postal_categories_overall_count
  
  DummyData <- Plot_Data%>%
    mutate(Position=ifelse(Status=="Scrutiny_Accepted",value+value[Status=="Scrutiny_Rejected"],value))%>%
    mutate(Extreme=max(value)*1.15)
  
  
  
  Plot_Data$Display <- factor(Plot_Data$Display,
                              levels=c("Scrutiny",
                                       "PVA Fulfilled",
                                       "PVA Accepted"))
  
  postal.reject.count <- ggplot(Plot_Data,
                                aes(x    = Display,
                                    y    = value,
                                    fill = Status)) +
    
    geom_bar(stat = "identity") +
    
    
    
    scale_fill_manual(breaks=c("PVA_Accepted", "PVA_Fulfilled", "Scrutiny_Accepted","Scrutiny_Rejected"),
                      labels=c("PVA Accepted", "PVA Fulfilled", "Scrutiny Accepted","Scrutiny Rejected"),
                      values=brewer.pal(4,"Paired")) +
    coord_flip() +
    ylab("") +
    xlab("") +
    
    theme_classic(base_size = 16) +
    ylim(c(0,  max(Postal_categories_overall_count$value)*1.05)) +
    
    theme(plot.margin     = unit(c(1,1,1,1), "cm"),
          plot.title      = element_text(vjust = 5, size = 15, face = "bold"),
          axis.text.x     = element_text(size  = 10),
          axis.title.x    = element_text(size  = 10),
          
          
          axis.title.y    = element_text(size  = 10),
          axis.text.y     = element_text(size  = 10),
          
          legend.position = 'bottom',
          legend.text     = element_text(size = 10),
          legend.title    = element_blank(),
          
          plot.subtitle   = element_text(size = 10, hjust = 0.5, face = "italic", color = "black"),
          plot.caption    = element_text(size = 10, hjust = 0.5, face = "italic", color = "black")) +
    
    geom_text(data=DummyData,
              aes(label = value,
                  hjust = -0.25,
                  y= Position,
                  x=Display),
              color=brewer.pal(4,"Paired"),
              size      = 4) +
    
    geom_blank(data=DummyData)
  
  postal.reject.count
  
} else {
  message('No data for graph, create message instead of plot')
  postal.reject.count <-'Insufficient data for graph, try again later :]'
  postal.reject.count
}

```



Total Provisional Markoffs
==============================================================================


Column  
-------------------------------------



```{r Markoffs-data_n_chart, fig.width=15, fig.height=10, fig.align='center'}
if(Dec_Votes_Available) {
  
  markoffs.cumul.linplot <- ggplot(EMA_markoff_group_date%>%
                                     mutate(LastLabel=ifelse(Date == max(Date), Total_cum_markoff, NA)), 
                                   aes(x=Date, 
                                       y=Total_cum_markoff,
                                       colour=Vote_type)) +
    geom_line(size = 3) +
    facet_wrap(vars(Vote_type),
               nrow=2,ncol=1,scales='free')+
    
    geom_point(size = 5, colour = 'grey') +
    
    theme_light(base_size = 16) +
    ylab("Provisional Mark-offs") +
    labs(title   = "Cumulative Declaration Votes Issued at Pre-Poll Voting Offices") +
    geom_text(aes(label=LastLabel,
                  vjust=2),
              size=5)+
    scale_x_date(date_labels    = "%b-%d", date_breaks = "1 day") +
    
    theme(plot.margin     = unit(c(1, 1, 1, 1), "cm"),
          plot.title      = element_text(vjust  = 5,        size  = 25,     face  = "bold"),
          axis.text.x     = element_text(size   = 15,       angle = 45,     hjust = 1, vjust = 1),
          axis.title.x    = element_text(size   = 20,       face  = "bold", vjust = -5),
          axis.line       = element_line(colour = 'black',   size = 0),
          strip.text      = element_text(size   = 15,        face = 'bold', colour='black'),
          strip.background = element_rect(color = "black",   fill = "white"),
          legend.position = 'none',
          
          axis.title.y  = element_text(size = 20, face = "bold", vjust = 4),
          axis.text.y   = element_text(size = 10),
          plot.subtitle = element_text(size = 20, hjust = 0.5, face = "italic", color = "black"),
          plot.caption  = element_text(size = 20, hjust = 0.5, face = "italic", color = "black"))
  
  markoffs.cumul.linplot
  
} else {
  message('No data for graph, create message instead of plot')
  markoffs.cumul.linplot <- 'Insufficient data for graph, try again later :]'
  markoffs.cumul.linplot
}

```





Enrolment/NAMAV Scrutiny Table
========================================================

Column {data-width = 800}
-------------------------------------


```{r Scrutiny-Table}
if (Dec_Votes_Available) {
  
  datatable(DecVote_master %>% 
              
              arrange(-Total_markoffs) %>%
              dplyr::select(-c("Updated","Total_markoffs")) %>%
              
              ## setrejection rate to a proportion.
              mutate(Rejection_rate =
                       percent(Rejection_rate))%>%
              
              #move Total Markoffs to after Rejected
              
              relocate(Scrutinised,.after=Rejected_markoffs)%>%
              
              ## Rename columns for better viewing.
              rename(`Venue Type`           = Venue_type,
                     `Enrolment Issued`     = Enrolment_envelopes,
                     `NAMAV Issued`         = NAMAV_envelopes,
                     `Total Scrutinised`    = Scrutinised,
                     `Provisional Markoffs` = Provisional_markoffs,
                     `Accepted/Area Only`   = Accepted_markoffs,
                     `Rejected`             = Rejected_markoffs,
                     `Awaiting Scrutiny`    = Unscrutinised,
                     `Rejection Rate`       = Rejection_rate),
            
            ## Change rownames
            rownames   = FALSE,
            extensions = 'Buttons',
            filter     = 'top',
            caption    = htmltools::tags$caption(
              
              ## Move captions to the bottom
              ## Does not seem possible to add line breaks to caption.
              style = 'caption-side: bottom; text-align: center;',
              
              'Venue-level Declaration Vote Scrutiny Information. 
                        Total Scrutinised = Accepted + Rejected. 
                        Unscrutinised = Decvotes remaining to be scrutinised.
                        Rejection Rate = Rejected/Total Scrutinised'),
            
            options = list(
              pageLength = 10,
              dom = 'Btip',
              buttons=c( 'csv', 'excel'),
              scrollY = '100%'),
            
            height = '600px')%>%
    formatStyle(columns=rep(1:length(DecVote_master)),fontSize="9pt")
} else {
  print("No Data Available")
}


```



Postal Scrutiny Table
========================================================


Column {data-width = 500}
-------------------------------------


```{r Postal-fulfillment-table}

if (Postal_Votes_Available){
  
  ## nrow(postal_reject_tab %>% distinct());nrow(postal_reject_tab)
  datatable(Postal_master_council %>% 
              
              ## Get the columns
              dplyr::select(Council, PVA_Accepted, PVA_Fulfilled,
                     Scrutiny_Accepted, Scrutiny_Rejected) %>%
              
              ## For Postal Vote Scrutiny Reject reasons, it will be the number of rejected PVCs divided 
              ## by the total number of votes scrutinised in that councilc()
              mutate(Rejection_rate = Scrutiny_Rejected/
                       (Scrutiny_Accepted + Scrutiny_Rejected)) %>%
              arrange(-Rejection_rate) %>%
              
              ## Set rejection rate to a proportion.
              mutate(Rejection_rate =
                       percent(Rejection_rate, accuracy = 1)) %>%
              
              ## Rename for ease of reading
              rename(`PVAs Accepted`      = PVA_Accepted,
                     `PVPs Fulfilled`     = PVA_Fulfilled,
                     `PVCs Accepted`      = Scrutiny_Accepted,
                     `PVCs Rejected`      = Scrutiny_Rejected,
                     `Council`            = Council,
                     `PVC Rejection Rate` = Rejection_rate),
            
            rownames   = FALSE,
            extensions = 'Buttons',
            filter     = 'top',
            
            caption    = htmltools::tags$caption(
              
              ## move captions to the bottom
              style = 'caption-side: bottom; text-align: center;',
              'Cumulative Postal Voting Figures for each Contest Area' ),
            
            options    = list(pageLength = 10,
                              dom        = 'Btip',
                              buttons   = c( 'csv', 'excel'),
                              scrollY = '100%'),
            height     = '600px')%>%
    formatStyle(columns = rep(1:length(postal_scrutiny_reject)), fontSize = "9pt")
} else {
  print("No Data Available")
}

```



Postal Reject Reasons
========================================================


Column 
-------------------------------------

**Note:** Due to the use of multiple reject reasons the total figures here may not match overall 
figures featured elsewhere.

```{r Postal-Rejection-Table}

if (exists("postal_reject_tab")) {
  ## nrow(postal_reject_tab %>% distinct());nrow(postal_reject_tab)
  datatable(postal_reject_tab %>% 
              arrange(-Count) %>%
              
              ## set rejection rate to a proportion.
              mutate(Percent_of_Applications =
                       percent(Percent_of_Applications, accuracy = 1)) %>%
              
              ## Remname columns for better reading
              dplyr::select(Council,
                     `Reject Reason`                   = Reject_reason,
                     `No. of Rejected PVAs`            = Count,
                     `Percent of Council Applications` = Percent_of_Applications),
            
            rownames   = FALSE,
            extensions = 'Buttons',
            filter     = 'top',
            caption    = htmltools::tags$caption(
              
              ## move captions to the bottom
              style = 'caption-side: top; text-align: center;',
              'Count of Postal Vote Application Reject Reasons'),
            
            options      = list(
              pageLength = 5,
              dom        = 'Btip',
              buttons    = c( 'csv', 'excel'),
              scrollY = '100%'),
            height       = '600px')%>%
    formatStyle(columns = rep(1:length(postal_reject_tab)), fontSize = "9pt")
} else {
  print("No Data Available")
}

```


<br>
<DIV STYLE="background-color:#000000; height:5px; width:100%;">
<br>


```{r Postal-Scrutiny-Table}

## nrow(postal_reject_tab %>% distinct());nrow(postal_reject_tab)
if (nrow(postal_scrutiny_reject) > 0){
  datatable(postal_scrutiny_reject %>% 
              # arrange(-Count) %>% 
              # na.omit()%>%
              # set rejection rate to a proportion.
              mutate(Percent_of_Scrutinized=
                       percent(Percent_of_Scrutinized, accuracy= 1)) %>%
              ## Change names for better reading
              dplyr::select(Council,
                     `Reject Reason`= Reject_reason,
                     `No. of Rejected PVCs`=Count,
                     `Percent of Council Scrutinised` = Percent_of_Scrutinized),
            
            rownames   = FALSE,
            extensions = 'Buttons',
            filter     = 'top',
            caption    = htmltools::tags$caption(
              
              ## Move captions to the bottom
              style = 'caption-side: top; text-align: center;',
              'Counts of Postal Vote Scrutiny Reject Reasons'),
            
            options      = list(
              pageLength = 5,
              dom        = 'Btip',
              buttons    = c( 'csv', 'excel'),
              scrollY = '100%'),
            height       = '600px') %>%
    formatStyle(columns = rep(1:length(postal_scrutiny_reject)), fontSize = "9pt")
} else {
  print("No Data Available")
}

```




