---
title: "BallotTrack"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    # self_contained: false
---


<style> 

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 80px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table { 
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)

```



<!-- RO Scan-in from Printer -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of carton scans - Returning Office/STH/CPVC Scan-in from Printer ** -->

<!-- ```{r} -->

<!-- ## View here -->
<!-- datatable(RO_2.0_scan_in_from_printer %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`),  -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_2.0_scan_in_from_printer)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ``` -->






<!-- RO Scan Out to venue -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of carton scans - Returning Office Scan-out to Venue ** -->

<!-- ```{r} -->

<!-- datatable(RO_3.0_scan_out_to_venue %>% -->

<!--             ##  -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`),  -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_3.0_scan_out_to_venue)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ``` -->





<!-- RO Scan-in from Venue -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of scans - Returning Office Scan-in from Venue ** -->

<!-- ```{r} -->

<!-- datatable(RO_4.0_scan_in_from_venue %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`), -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_4.0_scan_in_from_venue)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->


<!-- ``` -->





<!-- RO Scan-out to Count Centre -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of scans Returning Office Scan-out to Count Centre ** -->

<!-- ```{r} -->

<!-- datatable(RO_5.10_scan_out_to_CC %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`), -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_5.10_scan_out_to_CC)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ``` -->






<!-- Count Centre Scan-in from RO -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of scans Count Centre Scan-in from Returning Office ** -->

<!-- ```{r} -->

<!-- datatable(RO_5.11_scan_from_RO_to_CC %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`), -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_5.11_scan_from_RO_to_CC)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ``` -->






<!-- RO Scan-out to Warehouse  -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of scans - Returning Office Scan-out to Warehouse ** -->

<!-- ```{r} -->

<!-- datatable(RO_5.0_scan_out_to_Ware %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`), -->

<!--           rownames     = FALSE,  -->
<!--           extensions   = 'Buttons',  -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_5.0_scan_out_to_Ware)), fontSize = "9pt") %>%  -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ## Final message -->
<!-- message('All BallotTrack RMD code run') -->

<!-- ``` -->





<!-- Count Centre Scan in to ULD -->
<!-- ===================================== -->


<!-- Column {data-width = 800} -->
<!-- ------------------------------------- -->

<!-- ### **Progress of scans - Count Centre Scan Carton into ULD ** -->

<!-- ```{r} -->

<!-- datatable(RO_5.14_CC_scan_in_to_ULD %>% -->

<!--             ## Sort columns -->
<!--             arrange(`RO Name`, -->
<!--                     `ContestType`, -->
<!--                     `UseCase`, -->
<!--                     `ContainerType`), -->

<!--           rownames     = FALSE, -->
<!--           extensions   = 'Buttons', -->
<!--           filter       = 'top', -->

<!--           options      = list( -->
<!--             pageLength = 10, -->
<!--             dom        = 'Btip', -->
<!--             buttons    = c( 'csv', 'excel')), -->
<!--           height       = '600px') %>% -->

<!--   formatStyle(columns = rep(1:length(RO_5.14_CC_scan_in_to_ULD)), fontSize = "9pt") %>% -->
<!--   formatPercentage(c("PercentScanned",  "PercentRemaining"), digits = 1) -->

<!-- ## Final message -->
<!-- message('All BallotTrack RMD code run') -->

<!-- ``` -->


<!-- All Data -->
<!-- ===================================== -->


Column {data-width = 500}
-----------------------------------------------------------------------

```{r BallotTrack-RO, out.height="100%"}

if (exists("RO_Ballot_Track")){
  
RO_BallotTrack_Datatable <- datatable(RO_Ballot_Track,

          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(

            ## move captions to the bottom
            style = 'caption-side: bottom; text-align: center;',
            "Pre-Poll Mark-offs per venue per contest. All numbers are cumulative totals.
                        Proportion of Expected = Early Voting/Projected Vote
                        (i.e. the proportion, 200% = double the expected
                        amount of people have voted on that venue so far)"),

          options = list(
            pageLength = 15
            ,dom = 'Blfrtip'
            ,  scrollY = '100%'),
          fillContainer = TRUE

          , height = '600px')

RO_BallotTrack_Datatable

}

```
