---
title: "DecVoting"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    # self_contained: false
---


<style> 

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 80px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table { 
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)

```



Column {data-width = 500}
-----------------------------------------------------------------------

```{r Scrutiny-RO,out.height="100%"}

if (exists("RO_DecVotes")){
datatable(RO_DecVotes %>% 
            arrange(-Total_markoffs)%>%
            select(-Updated)%>%
            
            #setrejection rate to a proportion.
            
            mutate(Rejection_rate=
                     percent(Rejection_rate))%>%
            
            ## Rename columns for better viewing.
            rename(`Venue Type`             = Venue_type,
                   `Enrolment Envelopes`    = Enrolment_envelopes,
                   `NAMAV Envelopes`        = NAMAV_envelopes,
                   `Total Markoffs`         = Total_markoffs,
                   `Provisional Markoffs`   = Provisional_markoffs,
                   `Accepted Envelopes`      = Accepted_markoffs,
                   `Rejected Envelopes`      = Rejected_markoffs,
                   `Unscrutinised Envelopes` = Unscrutinised,
                   `Rejection Rate`         = Rejection_rate),
          
          ## Change rownames
          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(
            
            ## Move captions to the bottom
            ## Does not seem possible to add line breaks to caption.
            style = 'caption-side: bottom; text-align: center;',
            
            'Venue-level Declaration Vote scrutiny information.  
                        Unscrutinised = Decvotes remaining to be scrutinised.
                        Rejection Rate = Rejected Markoffs/Accepted Markoffs'),
          
          options = list(
            pageLength = 10,
            dom = 'tip'
             ,scrollY = '100%'),
          
          height = '600px')%>%
  formatStyle(columns=rep(1:length(RO_DecVotes)),fontSize="9pt")
} else {
  cat("No data available yet")
}


```
