---
title: "Pre-Poll"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    # self_contained: false
---


<style> 

.bluebox {
background-color: #ffffff;
border: solid #ddd 1px;
font-size: 15px;
height:40px;
padding:5px;
margin-bottom: 5px;
border-radius:5px;
color: #f9f9f9;
}

body {
padding-top: 80px !important;
font-family: Helvetica;
background-color: #ffffff;
font-size: 10pt;
}

/* Headers */
h1,h2,h3,h4,h5,h6{
font-size: 10pt;
font-family: Helvetica;
}

h1 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}

h2 {
font-weight: bold;
font-family: Helvetica;
font-size: 10px;
}


.leaflet-control-attribution{
display:none;
}



.btn {
background-color: DodgerBlue;
border: none;
color: white;
cursor: pointer;
font-size: 10px;
display: none;
}

.btn:hover {
background-color: #3d6ece;
}

table { 
border-spacing: 5px;
border-collapse: separate;
border:1px
}


div.header{

padding-top:0px;

}


div.main-container { max-width: 50%; }
table.table-condensed {width:100%}


div.footer {
position: sticky;
bottom: 0;
width: 100%;
height:30px;
background-color: #2b6eda;
color: white;
text-align: center;
}

div.main-wrapper {
position: relative;
}


div.leaflet-control-attribution{
display:none;
}

div.leaflet-container {
background: #0184a9;
}



</style>


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)

```



Column {data-width = 500}
-----------------------------------------------------------------------

```{r Pre-Poll-RO,out.height="100%"}

if (exists("RO_Markoffs")){
RO_Markoff_Datatable<-datatable(RO_Markoffs %>%

            #set proj_Prop to projection.

            #mutate(Proj_Prop= percent(Proj_Prop, accuracy=0.1))%>%

            rename(Council=ISSUINGAREA,
                   Ward =CONTESTAREA,
                   `Contest Type`=CONTESTTYPECODE,
                   `Venue Name`=VENUENAME,
                   `Pre-poll Markoffs`=Pre_Poll_Markoffs,
                   `Pre-poll Projections`=Cum_Projection,
                   `Proportion of Expected`=Proj_Prop),

          rownames   = FALSE,
          extensions = 'Buttons',
          filter     = 'top',
          caption    = htmltools::tags$caption(

            ## move captions to the bottom
            style = 'caption-side: bottom; text-align: center;',
            "Pre-Poll Mark-offs per venue per contest. All numbers are cumulative totals.
                        Proportion of Expected = Pre-poll markoffs/ Pre-poll Projections’ 
                        (i.e. the proportion, 200% = double the expected
                        amount of people have voted on that venue so far)"),

          options = list(
            pageLength = 15
            ,dom = 'tip'
            , scrollY = '100%'),
          fillContainer = TRUE

          , height = '600px'
          )%>%
  #set to format as percentage
  formatPercentage(c('Proportion of Expected'),1)

RO_Markoff_Datatable
# p <- ggplot(mtcars, aes(wt, mpg))
# p + geom_point()

} else {
  print("No data available yet")
}

```
